### 2015-10-02 pics/blue.tex
start full paper

\begin{tikzpicture}[scale=1.0]

\begin{axis}[%scale=1.5,
             domain=0:12.0,
             restrict expr to domain={x}{0:12.0},
             %restrict expr to domain={y}{1.0E-12:7},
             xlabel={$E$ [eV]},
%             xmin=0,
%             xmax=1.5,
             ymin=0,
%             ymax=7,
             %xtick={30,50,...,170},
             %xticklabels={2,4,6,8,10,12,15,20,25},
             %ytick={-1.0,-0.8,...,1.0},
             %yticklabels={1.0,0.8,0.6,0.4,0.2,0.0,0.2,0.4,0.6,0.8,1.0},
             ylabel={$\Gamma$ [eV]},
             scale only axis,
             width=\textwidth-1.5cm,
             height=8cm,
             %ybar stacked
             axis line style = very thick,
             tick style = very thick
             ]

\addplot+[ycomb,
         mark=.,
         ultra thick,
         diplom2,
         forget plot
        ]
        table[
        x expr = \thisrowno{0},
        y expr = \thisrowno{1}
        ]
        {../data/blue_NeNe.dat};
        \addlegendimage{line legend, diplom2, very thick};
        \addlegendentry{blue};

%\addplot[
%         mark=none,
%         diplom2,
%         ultra thick,
%         %dotted
%         ]
%         table[
%         x expr=\thisrowno{0},
%         y expr=\thisrowno{1}
%         ]
%        {../data/xear_3_surf.dat_intadd.inp.sp};
%         \addlegendentry{1 Xe, 55 Ar};
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{axis}
\end{tikzpicture}

### 2015-10-02 clusters.tex
add all section files

\section{ICD in Clusters}

\subsection{NeAr Clusters}

\subsection{Icosahedral vs. fcc Structure of Clusters}

### 2015-10-02 partners.tex
add all section files

\section{Decay with Decay Partners at Different Distances}

### 2015-10-05 clusters.tex
add pictures and first introduction

@@
 \subsection{NeAr Clusters}
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=\columnwidth]{pics/rot.pdf}\\
+ \includegraphics[width=\columnwidth]{pics/blue.pdf}
+ \caption{ICD spectra for the NeNe-ICD part of the structures of set 3 and
+          set 5 of the NeAr clusters in Ref. \cite{Fasshauer14_1}
+          plotted as stick spectra.
+          The different peak groups resemble different pair types
+          within the NeAr clusters. The lowest energy peaks (\textbf{a})
+          refer to nearest neighbours
+          of different shells, the peak group \textbf{b} refers
+          to nearest neighbours within one shell and the peak group \textbf{c}
+          refers to next nearest neighbours between different shells.
+          The peaks in group \textbf{d} contain both peaks stemming from
+          pairs within the same shell as well as pairs consisting of atoms
+          of different shells.}
+ \label{figure:rot}
+\end{figure}
+
+%\begin{figure}
+% \centering
+% \includegraphics[width=\textwidth]{pics/blue.pdf}
+% \caption{}
+% \label{figure:blue}
+%\end{figure}
 
 \subsection{Icosahedral vs. fcc Structure of Clusters}
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=\columnwidth]{pics/reinNe}
+ \caption{ICD spectra of pure neon clusters consisting of 55 atoms in
+          icosahedral and fcc structure. In clusters with an ideal fcc structure
+          all interatomic distances are the same and hence only one peak
+          for each shell around any atom in the cluster is to be expected.
+          In ideal icosahedral clusters the interatomic distances between atoms
+          within the same shell and between atoms in neighbouring atoms
+          are different. Therefore two peaks for interactions partners
+          at different distances can be expected. This feature might
+          help to experimentally identify the underlying structure of clusters.}
+ \label{figure:reinNe}
+\end{figure}

### 2015-10-05 computational.tex
add pictures and first introduction

\section{Computational Details}

\begin{table}[!h]
 \caption{Experimental values for the single ionization potentials
          \cite{Fasshauer14_1}
          used for the estimation of the decay widths.}
 \label{table:exp_input}
 \centering
 \begin{tabular}{lc}
  \toprule
  indicator            &  value \\
  \midrule
  SIP(Ne2s)            &  \unit[47.75]{eV} \\
  SIP(Ne2p)            &  \unit[21.10]{eV} \\
  SIP(Ar3p)$_{c<3}$    &  \unit[15.40]{eV} \\
  SIP(Ar3p)$_{c\ge 3}$ &  \unit[15.20]{eV} \\
  \bottomrule
 \end{tabular}
\end{table}

### 2015-10-05 intro.tex
add pictures and first introduction

\section{Introduction}

The Interatomic Coulombic Decay (ICD) is an electronic decay process of an atom or
molecule (a unit) involving atoms or molecules of the environment. After an
ionization from the sub-valence region of a unit $A$, the vacancy is filled
by an electron of the same unit and the excess energy is transferred to a decay
partner $B$, which subsequently get ionized:

\begin{equation*}
 A^+ + B \rightarrow A^+ + B^+ + e^-_{ICD}  .
\end{equation*}

The two units $A$ and $B$ are both positively charged, reppel each other and
thereby undergo a Coulomb explosion. This process was predicted theoretically
\cite{Cederbaum97} and later proven experimentally \cite{Marburger03}. Since then
it has been studied in a multitude of different systems such as small and large
rare gas clusters \cite{many,Fasshauer14_1},
clusters of small molecules \cite{},
quantum dots \cite{Bande13}
and proteins \cite{Harbach13}. Additionally it has given raise to
the investigation of a whole zoo of ICD-like processes (see Ref. \cite{}
and references therein).

The ICD process was so far mostly discussed for the case of decay partners in
the direct vicinity, because the decay widths with decay partners further away
was considered to be negligible. We showed that they need to be included
for larger systems with many decay partners \cite{Fasshauer13} and that the
corresponding peaks are also experimentally observable \cite{Fasshauer14_1}
(see Figure \ref{figure:near_spectra}).
However, this feature has so far not been addressed by itself. We will
therefore first discuss the distance dependency of the ICD in general
in section \ref{} and then
zoom in on the NeNe ICD part of the ICD spectra of NeAr clusters in section
\ref{}. Here we will discuss the peaks and their origin in detail and thereby
raise the question, what a \emph{nearest neighbour} is supposed to be. From
our conclusions we propose the possibility to distinguish cluster structures
of ideal icosahedral and fcc structures using ICD spectra in section \ref{}.

\begin{figure}[h]
 \centering
 \includegraphics[width=\columnwidth]{pics/2dim_coincs.eps}\\
 \includegraphics[width=\columnwidth]{pics/NeArcluster_theospecs.pdf}
 \caption{Experimental and theoretical NeAr ICD spectra \cite{Fasshauer14_1}.
          The experimental spectra were obtained for different cluster expansion
          conditions and the theoretical spectra were obtained for different
          underlying cluster structures. In both the NeNe and the NeAr ICD part
          of the spectrum a main peak and next to it at least one more peak at
          higher energies are observed. These smaller peaks stem from decays
          with decay partners at larger distances \cite{Fasshauer13,Fasshauer14_1}.}
 \label{figure:near_spectra}
\end{figure}

### 2015-10-05 partners.tex
add pictures and first introduction

@@
 \section{Decay with Decay Partners at Different Distances}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=\columnwidth]{pics/model_RE.pdf}
+ \caption{Kinetic energy of the ICD electron depending on the interatomic
+          distance of the two atoms involved in the decay within the
+          asymptotic approximation. The kinetic energy shows a $1/R$
+          behaviour and hence distance changes at small distances lead
+          to larger changes in the kinetic energy than at larger distances.}
+ \label{figure:model_RE}
+\end{figure}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=\columnwidth]{pics/model_RGamma.pdf}
+ \caption{Decay widths for different interatomic distances following an
+          asymptotic $1/R^6$-behaviour. For distances larger than twice
+          the shortest distance considered the peaks are not visible in this
+          plot.}
+ \label{figure:model_RGamma}
+\end{figure}
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[width=\columnwidth]{pics/model_EGamma.pdf}
+ \caption{ICD electron spectrum for interaction partner distances of
+          \unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[11]{\AA}.
+          The energy difference between equidistant interaction partners
+          decreases with increasing distance. For the case of Ne$_2$ pairs
+          these energy differences between the peaks stemming from different
+          interatomic distances are given by:
+          \unit[3]{\AA},\unit[4]{\AA} $\rightarrow$ \unit[1.20]{eV},
+          \unit[4]{\AA},\unit[5]{\AA} $\rightarrow$ \unit[0.68]{eV} and
+          \unit[5]{\AA},\unit[6]{\AA} $\rightarrow$ \unit[0.48]{eV}.
+          This means that the spectrum is better resolved for smaller distances
+          and that small distance changes like vibrations will mainly affect
+          this lower energy part of the spectrum.
+}
+ \label{figure:model_EGamma}
+\end{figure}
+
+%\begin{figure}
+% \centering
+% \includegraphics[width=\textwidth]{pics/}
+% \caption{}
+% \label{}
+%\end{figure}

### 2015-10-05 theory.tex
add pictures and first introduction

\section{Theoretical Background}

\begin{align}
 E_{in}        &= SIP(X_{in}) \label{equation:E_in}\\          
 E_{fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
           \label{equation:E_fin}\\                            
 E_{sec}^\beta &= E_{in}^\beta - E_{fin}^\beta \label{equation:E_sec}         
\end{align}

following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
and Fano \cite{Fano61}

\begin{equation}
 \Gamma_{\beta}(E_{res}) = 2\pi \left|
                           \braket{\Phi_{in}| H_f |\chi_{\beta}}
                           \right|^2
\end{equation}

### 2015-10-05 pics/blue.tex
add all figures
add more pics

@@
          ultra thick,
-         diplom2,
+         blue,
          forget plot
@@
         {../data/blue_NeNe.dat};
-        \addlegendimage{line legend, diplom2, very thick};
-        \addlegendentry{blue};
+        \addlegendimage{line legend, blue, very thick};
+        \addlegendentry{set 3 (blue)};
 
-%\addplot[
-%         mark=none,
-%         diplom2,
-%         ultra thick,
-%         %dotted
-%         ]
-%         table[
-%         x expr=\thisrowno{0},
-%         y expr=\thisrowno{1}
-%         ]
-%        {../data/xear_3_surf.dat_intadd.inp.sp};
-%         \addlegendentry{1 Xe, 55 Ar};
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\draw[thick] (axis cs:1.45,0.003) arc [radius=0.80cm,start angle=10,end angle=170];
+\node[pin={[pin distance=0.2cm]90:{\small across shells}}]
+     at (axis cs:1.1,0.0038) {};
+
+\draw[thick] (axis cs:2.00,0.0078) arc [radius=0.50cm,start angle=10,end angle=170];
+\node[pin={[pin distance=0.2cm]10:{\small same shell}}]
+     at (axis cs:2.0,0.0080) {};
+
+\draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
+\node[pin={[pin distance=0.2cm]92:{\small across shells}}]
+     at (axis cs:2.70,0.0010) {};
 

### 2015-10-05 pics/rot.tex
start full paper
add all figures
add more pics

--- 2015-10-02 pics/blue.tex
@@
          ultra thick,
-         diplom2,
+         red,
          forget plot
@@
         ]
-        {../data/blue_NeNe.dat};
-        \addlegendimage{line legend, diplom2, very thick};
-        \addlegendentry{blue};
+        {../data/red_NeNe.dat};
+        \addlegendimage{line legend, red, very thick};
+        \addlegendentry{set 5 (red)};
 
-%\addplot[
-%         mark=none,
-%         diplom2,
-%         ultra thick,
-%         %dotted
-%         ]
-%         table[
-%         x expr=\thisrowno{0},
-%         y expr=\thisrowno{1}
-%         ]
-%        {../data/xear_3_surf.dat_intadd.inp.sp};
-%         \addlegendentry{1 Xe, 55 Ar};
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\draw[thick] (axis cs:1.40,0.007) arc [radius=0.77cm,start angle=10,end angle=170];
+\node[pin={[pin distance=0.2cm]90:{\small across shells}}]
+     at (axis cs:1.0,0.0080) {};
+
+\draw[thick] (axis cs:1.90,0.0120) arc [radius=0.55cm,start angle=10,end angle=170];
+\node[pin={[pin distance=0.2cm]10:{\small same shell}}]
+     at (axis cs:1.9,0.0125) {};
+
+\draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
+\node[pin={[pin distance=0.2cm]92:{\small across shells}}]
+     at (axis cs:2.70,0.0010) {};
 

### 2015-10-16 intro.tex
more details in the introduction

@@
 
-The two units $A$ and $B$ are both positively charged, reppel each other and
+The two units $A$ and $B$ are both positively charged, repell each other and
 thereby undergo a Coulomb explosion. This process was predicted theoretically
@@
 
+In order to undergo an ICD and it to be observable, two criteria have to
+be fulfilled: the energy and the coupling criterion. The energy criterion
+requires the energy conservation to hold. In case the doubly ionized final
+state is higher in energy than the singly ionized initial state, the ICD
+is energetically forbidden. The coupling criterion requires the decay
+process to be sufficiently efficient to outperform other decay pathways
+such as radiative decay by emission of a photon or coupling to the nuclear
+degrees of freedom in molecules. The property calculted for this is the
+decay width $\Gamma = \frac{\hbar}{\tau}$, which is inversely proportional
+to the lifetime $\tau$ and proportional to the decay rate $\frac{1}{\tau}$.
+
 The ICD process was so far mostly discussed for the case of decay partners in
 the direct vicinity, because the decay widths with decay partners further away
-was considered to be negligible. We showed that they need to be included
-for larger systems with many decay partners \cite{Fasshauer13} and that the
-corresponding peaks are also experimentally observable \cite{Fasshauer14_1}
-(see Figure \ref{figure:near_spectra}).
-However, this feature has so far not been addressed by itself. We will
+was considered to be negligible. Therefore, the decay was studied in clusters
+up to 13 neon atoms considering the initial ionization of only the central
+atom and not the other ones \cite{Santra01_3}. In this study, a higher than
+linear dependence of the decay width on the number of neighbours was
+observed. A linear dependence would be expected for equally decay partners
+at equal distances from the initially ionized atom in the same environment.
+Since the decay width in the asymptotic limit shows an 
+$1/\omega^{4}_{vp}$-behaviour on the energy of the virtual photon, which
+is decreased for a stabilized final state, this additional feature
+can be related to
+the better energetic stabilization of the doubly ionized
+final state in larger clusters \cite{Fasshauer13}.
+
+We showed that decay pathways with decay partners at larger distances need to
+be included for larger systems with many decay partners for two reasons:
+\begin{enumerate}
+ \item In cluster structures more than one pair of units can consist of
+       the same atom types and have the same interatomic distance. Hence,
+       they are indistinguishable in the spectrum. Since the decay rate
+       is proportional to the number of such pairs as well as the peak
+       intensity, the peaks stemming from several pairs are favoured
+       compared to other ones at similar distances. Therefore, peaks
+       stemming from decays with distant decay partners can be visible
+       in ICD spectra of clusters. \cite{Fasshauer14_1}
+ \item The opening of ICD-like decay channels depend on the interatomic
+       distance. A channel being closed at the distance to the most direct
+       beighbours might be open for interaction partners at slightly
+       larger distances. If this particular decay channel is more efficient
+       than other decay channels being open for the decay with direct
+       neighbours, it can still be visible in the spectrum or even
+       outperform the slower decay pathways and hence they have to be
+       taken into account. We have shown this for the case of ICD vs.
+       the Electron Transfer Mediated Decay (ETMD3) process in mixed ArXe
+       clusters \cite{Fasshauer13,Fasshauer15_2}.
+\end{enumerate}
+However, this feature of non-nearest neighbour ICD
+has so far not been addressed by itself.
+
+Rare gas clusters are favourable test systems for basic features both
+from a theoretical and an experimental point of view. Their spherical
+symmetry and their very localized orbitals allow for an comparably easy
+theoretical description of the decay processes and the gaseous state
+of their components allows for a convenient cleaning of the experimental
+setup allowing for higher count rates and therefore a higher resolution
+of the spectra. However, the structure of the clusters reveals an
+interesting matter of research. Small, ideal clusters exhibit an icosahedral
+structure while large clusters have a face-centered-cubic (fcc) structure.
+It is still unclear at which cluster size the transition from a favourable
+icosahedral to an fcc structure is. Numbers in the range of 800--3000 atoms
+have been reported. \cite{}
+We propose to use the ICD to be a possible tool to differentiate between
+icosahedral and fcc cluster structures using the different distance
+patterns in the cluster structures.
+
+We will
 therefore first discuss the distance dependency of the ICD in general
-in section \ref{} and then
-zoom in on the NeNe ICD part of the ICD spectra of NeAr clusters in section
-\ref{}. Here we will discuss the peaks and their origin in detail and thereby
+in section \ref{sec:theory} and then
+zoom in on the NeNe ICD part of the ICD spectra of NeAr clusters
+\cite{Fasshauer14_1} in section \ref{sec:near}. Here we will discuss the
+peaks and their origin in detail and thereby
 raise the question, what a \emph{nearest neighbour} is supposed to be. From
 our conclusions we propose the possibility to distinguish cluster structures
-of ideal icosahedral and fcc structures using ICD spectra in section \ref{}.
+of ideal icosahedral and fcc structures using ICD spectra in
+section \ref{sec:icofcc}.
 
-\begin{figure}[h]
- \centering
- \includegraphics[width=\columnwidth]{pics/2dim_coincs.eps}\\
- \includegraphics[width=\columnwidth]{pics/NeArcluster_theospecs.pdf}
- \caption{Experimental and theoretical NeAr ICD spectra \cite{Fasshauer14_1}.
-          The experimental spectra were obtained for different cluster expansion
-          conditions and the theoretical spectra were obtained for different
-          underlying cluster structures. In both the NeNe and the NeAr ICD part
-          of the spectrum a main peak and next to it at least one more peak at
-          higher energies are observed. These smaller peaks stem from decays
-          with decay partners at larger distances \cite{Fasshauer13,Fasshauer14_1}.}
- \label{figure:near_spectra}
-\end{figure}
+%\begin{figure}[h]
+% \centering
+% \includegraphics[width=\columnwidth]{pics/2dim_coincs.eps}\\
+% \includegraphics[width=\columnwidth]{pics/NeArcluster_theospecs.pdf}
+% \caption{Experimental and theoretical NeAr ICD spectra \cite{Fasshauer14_1}.
+%          The experimental spectra were obtained for different cluster expansion
+%          conditions and the theoretical spectra were obtained for different
+%          underlying cluster structures. In both the NeNe and the NeAr ICD part
+%          of the spectrum a main peak and next to it at least one more peak at
+%          higher energies are observed. These smaller peaks stem from decays
+%          with decay partners at larger distances \cite{Fasshauer13,Fasshauer14_1}.}
+% \label{figure:near_spectra}
+%\end{figure}

### 2015-10-16 theory.tex
add labels

@@
 \section{Theoretical Background}
+\label{sec:theory}
+
+In roder to simulate the ICD electron spectra for a given cluster structure,
+the kinetic energies of the ICD electrons $E_{ICD}$ and the corresponding decay
+decay widths of all pairs have to be determined. The ICD electron energies
+are given by the differences between the initial state and the final state
+energies $E_{in}$ and $E_{fin}$, respectively. The initial state energy
+is given by the single ionization potential (SIP) of the sub-valence electron
+of the entire system
+and the final state energy is given by the double ionization potential (DIP).
+In the asymptotic limit, which is a reasonably good approximation for
+weakly bound systems, he initial state energy is approximated by the SIP
+of the initially ionized unit $X_{in}$ and the final state energy can be
+approximated
+by the sum over the SIPs of the electron donating unit $X_D$ and the electron
+emitting unit $X_E$ ionized in the final state as well as the
+Coulomb repulsion between two point charges at the interatomic distance $R$
 
 \begin{align}
+ E_{ICD}^\beta &= E_{in}^\beta - E_{fin}^\beta \label{equation:E_sec}\\
  E_{in}        &= SIP(X_{in}) \label{equation:E_in}\\          
- E_{fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1d
-           \label{equation:E_fin}\\                            
- E_{sec}^\beta &= E_{in}^\beta - E_{fin}^\beta \label{equation:E_sec}         
+ E_{fin}^\beta &= SIP(X_{D}^\beta) + SIP(X_{E}^\beta) + \frac 1R
+           \label{equation:E_fin}                . 
 \end{align}
+Here, $\beta$ denotes the selected decay channel.
 
-following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
-and Fano \cite{Fano61}
+Following Wentzel \cite{Wentzel27}, Feshbach\cite{Feshbach58,Feshbach62}
+and Fano \cite{Fano61} the decay width is given by
 
@@
                            \braket{\Phi_{in}| H_f |\chi_{\beta}}
-                           \right|^2
+                           \right|^2   .
 \end{equation}

### 2015-10-16 partners.tex
discuss general properties of decay at different distances

@@
 \section{Decay with Decay Partners at Different Distances}
+\label{sec:partners}
+
+To fully understand the spectra of clusters with several possible
+initially ionized atoms with multiple decay partners it is necessary to
+understand the properties of the decay of a single pairof atoms. As can be seen
+from Eq. (\ref{}), the kinetic energy of the ICD electron follows an
+$1/R$-behaviour shown in Figure \ref{figure:model_RE} for the case
+of a neon dimer at different distances.
 
@@
 \end{figure}
+From this diagram it can already be
+seen that the kinetic energies stemming from equidistant peaks of
+\unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[11]{\AA} are
+not equidistant in energy difference but rather increase it for an increasing
+interatomic distance.
+
+The corresponding decay widths $\Gamma$ depending on the interatomic
+distance are shown in figure \ref{figure:model_RGamma}. They show an
+asymptotic $1/R^6$-behaviour such that the decay widths from an interatomic
+distance of \unit[7]{\AA} on, the peaks are too small to be seen in the
+figure. This means that in case of a neon dimer with an internuclear distance
+of \unit[3]{\AA}, a decay with one decay partner at twice the internuclear
+distance of the neon dimer is very unlikely, but that interactions with
+decay partners at shorter distances can not in general be neglected.
 
@@
 \end{figure}
+
+A similar picture is given by the hypothetical ICD-electron spectrum for
+decay partners at distances of \unit[3]{\AA}, \unit[4]{\AA}, \dots,
+\unit[11]{\AA} shown in Figure \ref{figure:model_EGamma}. Here, the kinetic
+energy of the ICD electron is depicted on the abscissae while the decay
+width $\Gamma$ is plotted on the ordinate. Since the decay width is proportional
+to the decay rate and hence the decay propability, these spectra can directly
+be compared to experimental ICD electron spectra.
 
@@
 
+The first and dominant peak stems from the decay with a decay
+partner at a distance of \unit[3]{\AA}. The energy distance to the next peak
+stimmeng from a decay with a decay partner with an internuclear distance of
+\unit[4]{\AA} is found at a \unit[1.20]{eV} higher kinetic energy and the
+energy difference to the next peak stemming from a \unit[5]{\AA} distant
+decay partner is further \unit[0.68]{eV} higher. The increase of kinetic
+energy of the ICD electron is caused by a decrease of Coulomb repulsion between
+the interaction partners in the final state and therefore, the additional
+excess in energy is converted into kinetic energy of the emitted ICD electron.
+The energy difference between the peaks shown in Figure \ref{figure:model_EGamma}
+decreases with increasing distance of decay partners or kinetic energy
+of the ICD electron. This means that for smaller interatomic distances and
+comparably low kinetic energies of the ICD electron, the spectrum has a higher
+resolution based on the interatomic distance of the decay partners.
+Therefore, a peak structure might be visible for the decay with nearest
+neighbours (or the closest atoms with energetically allowed decay channels)
+but not necessarily for all different kinds of interaction partners at larger
+distances.
+
 %\begin{figure}

### 2015-11-15 intro.tex
more dteails about ico vs. fcc cluster structure

@@
 such as radiative decay by emission of a photon or coupling to the nuclear
-degrees of freedom in molecules. The property calculted for this is the
+degrees of freedom in molecules. The property calculated for this is the
 decay width $\Gamma = \frac{\hbar}{\tau}$, which is inversely proportional
@@
        neighbours, it can still be visible in the spectrum or even
-       outperform the slower decay pathways and hence they have to be
+       outperform the slower decay mechanism and hence they have to be
        taken into account. We have shown this for the case of ICD vs.
@@
 setup allowing for higher count rates and therefore a higher resolution
-of the spectra. However, the structure of the clusters reveals an
+of the spectra. At the same time, the structure of the clusters reveals an
 interesting matter of research. Small, ideal clusters exhibit an icosahedral
-structure while large clusters have a face-centered-cubic (fcc) structure.
-It is still unclear at which cluster size the transition from a favourable
-icosahedral to an fcc structure is. Numbers in the range of 800--3000 atoms
-have been reported. \cite{}
+structure while large clusters have a cuboctahedral structure, which
+infinitely extended yields the solid state face-centered-cubic (fcc) structure.
+In the solid state, every single atom is surrounded by twelve other atoms in the
+same distance. Surface atoms or even atoms at edges and vertices are rare
+compared to the number of atoms in the bulk. These atoms being surrounded
+by less than twelve atoms, are dominant in small clusters. Therefore,
+an icosahedral structure with a shorter distance between different shells and
+larger distances of atoms in the same shell, stabilizing surface atoms is
+energetically favourable in small clusters with a large surface-to-bulk ratio.
+Together with a structure change
+the clusters' properties gradually change towards those of solids and
+conductivity as well as magnetizability can be observed. \cite{Benfield92}
+It is still unclear at which cluster size the favourable structures changes from
+an icosahedral to an fcc structure. Numbers in the range of 800--3000 atoms
+have been reported. \cite{Hartke02,Pahl08}
 We propose to use the ICD to be a possible tool to differentiate between

### 2015-11-15 clusters.tex
add labels
discussion of results

@@
 \section{ICD in Clusters}
+\label{sec:clusters}
 
 \subsection{NeAr Clusters}
+We earlier studied how ICD can be utilized to determine the structure of
+heteroatomic rare gas clusters \cite{Fasshauer14_1} and thereby showed a clear
+geometry dependence of the ICD electron spectra. Using the simulations of
+cluster model structures, we were able to explain the shoulders of both
+the NeNe-ICD and the NeAr-ICD peak by decay with decay partners of the next
+shell. While the shoulder of the NeAr-ICD peak might be able to be explained
+by a decay of higher vibrational levels \cite{Scheit06}. However, in neon
+clusters no bound vibrational states exist \cite{}.
+Other decay processes resulting in secondary electrons of the corresponding
+kinetic energies between \unit[2.5]{eV} and \unit[3.5]{eV} are not known.
+Therefore, we can conclude that this shoulder stems from next shell ICD.
+In the following, we will zoom into the NeNe-ICD part of the spectra
+of Figure xyz of Ref. \cite{Fasshauer14_1} and analyze them in more detail.
+
+\label{sec:near}
 \begin{figure}[h]
@@
           of different shells.}
- \label{figure:rot}
+ \label{figure:rot_blue}
 \end{figure}
 
-%\begin{figure}
-% \centering
-% \includegraphics[width=\textwidth]{pics/blue.pdf}
-% \caption{}
-% \label{figure:blue}
-%\end{figure}
+In Figure \ref{figure:rot_blue} the ICD electron spectra for the NeNe-ICD
+part of heterogeneous clusters are shown as stick spectra
+for set 3 and set 5. Hereby, we stick to the color code of
+Ref. \cite{Fasshauer14_1}. Both spectra exhibit a similar pattern of peak groups.
+The groups are found around \unit[1.0]{eV} (group \textbf{a}),
+around \unit[1.7]{eV} (group \textbf{b}), around \unit[2.6]{eV} (group \textbf{c})
+and from \unit[3]{eV} to \unit[4]{eV} (group \textbf{d}). By comparing
+the interatomic distances, of which these peaks originate to their occurance
+in the cluster structures, the peak groups can be assigned to atom pairs
+within the cluster. For group \textbf{a} the peaks stem from decays
+between two nearest neighbour atoms of two different shells, while group \textbf{b}
+stems from the decay partners being nearest neighbours in the same shell.
+Group \textbf{c} can be assigned to next-nearest neighbours in adjacent shells
+and group \textbf{d} stems from a mixture of pairs which cannot unambigiously
+be categorized because different kinds of peaks intersect each other.
 
-\subsection{Icosahedral vs. fcc Structure of Clusters}
+Obviously, the peak groups have a fine structure which originates from
+different positions of the decay partners within a shell (face, egde or vertex).
+For the investigated ideal icosahedral structures, these pairs of group \textbf{a}
+are from low to high kinetic energies: vertex-vertex, edge-edge, edge-face and
+face-face. Due to vibrational broadening of the peaks the experimental observation
+of this fine structure is unlikely in neon clusters.
+
+Concluding these findings, there is not neccessarily only one kind of nearest
+neighbours in clusters. Even the next-nearest neighbours are closer to
+twice the interatomic distance of the closest pair with an open decay channel.
+Therefore, as formerly supposed, decay partners of twice the closest interatomic
+distance indeed have a very small contribution to the total spectrum. However,
+all other decay partners do have to be taken into account in order to simulate
+an ICD spectrum for clusters.
+
+\subsection{Icosahedral vs. Cuboctahedral Structure of Clusters}
+\label{sec:icofcc}
+We would like to recall that clusters with an icosahedral structure
+have shorter interatomic distances between shells then within the same
+shell.
+In terms of the ICD, different groups of nearest neighbours exist,
+one within the same shell and one
+between adjacent shells. This is characteristic for icosahedral cluster structures.
+Cuboctahedral cluster structures on the other hand are characterized by only
+one interatomic distance. 
+Therefore, icosahedral cluster structures should be distinguishable from
+cuboctahedral clusters by the number of peaks as shown in Figure
+\ref{figure:reinNe}.
+
 \begin{figure}[h]
@@
 \end{figure}
+
+Whether or not the cluster structures would be distinguishable in experiment
+will depend the vibrational broadening of the peaks, the experimental
+resolution and the distance difference and hence the energy difference of the
+peaks in the icosahedral structure. In this proof-of-principle discussion
+we chose neon clusters for comparison with experiment but for the distinction
+of cluster structures it might be recommendable to choose atoms with larger
+internuclear distances in clusters.

### 2015-11-15 computational.tex
add computational text

@@
 \section{Computational Details}
+The cluster structures used were constructed to have an ideal icosahedral or
+face-centered-cubic geometry with optional additional incomplete outermost
+shells. These are based on the van der Waals radii for neon
+$r_{Ne}=\unit[1.54]{\AA}$ \cite{}
+and argon $r_{Ar}=\unit[1.88]{\AA}$ \cite{}. In case of the NeAr clusters those
+two cluster structures from Ref. \cite{Fasshauer14_1} were used that matched best
+with the combination of the argon content in the cluster, the NeAr-ICD to total
+ICD ratio and the peak position of the NeAr-ICD peak. These are xyz
+for set 
+and xyz for set.
 
-\begin{table}[!h]
+\begin{table}[h]
  \caption{Experimental values for the single ionization potentials
@@
 \end{table}
+
+The calculations to obtain the ICD electron spectra of those cluster
+structures were performed with
+the program HARDRoC \cite{HARDRoC} using experimental ionization energies shown
+in Table \ref{table:exp_input} and curves fitted to the decay width of the
+NeNe ICD of Ref. \cite{}.

### 2015-11-15 theory.tex
describe decay widths in more detail

@@
 \end{equation}
+Here, the bound and ionized initial state is described by $\ket{\Phi_{in}}$ and
+the final continuum state of a particular decay channel $\beta$ is
+given by $\ket{\chi_{\beta}}$.
+This challenging description involving both bound and continuum states can
+amongst others be achieved by the FanoADC-Stieltjes approach, where a
+subset of the $2h1p$ functions within the Algebraic Diagrammatic Construction
+(ADC) are used to mimic the final state function $\ket{\chi_{\beta}}$.
+By these means calculated discrete energies and corresponding transitions
+moments are then used to construct a continuous function, which is evaluated
+at the resonance energy approximated by the single ionization potential
+corresponding to the initial state $E_{in}$. For a more detailed
+description of the method and comparison to other approaches see References
+\cite{Averbukh05,Fasshauer15_1} and references therein.

### 2015-11-30 clusters.tex
add corrections to entire manuscript

--- 2015-10-05 clusters.tex
@@
 \section{ICD in Clusters}
+\label{sec:clusters}
 
 \subsection{NeAr Clusters}
+\label{sec:near}
+After ionization from the Ne2s, a heteronuclear NeAr cluster can decay
+via two competing pathways:
+
+\begin{center}
+\begin{tabular}{lcr}
+ Ne(2s$^{-1}$) Ne &$\rightarrow$ & Ne(2p$^{-1}$) Ne(2p$^{-1}$)\\
+ Ne(2s$^{-1}$) Ar &$\rightarrow$ & Ne(2p$^{-1}$) Ar(3p$^{-1}$)
+\end{tabular}
+\end{center}
+
+in which the excess energy gained by filling the Ne2s vacancy is transferred to
+either another neon atom or to an argon atom. Since the lifetimes of the
+NeNe-ICD and the NeAr-ICD are of the same order of magnitude, both are
+visible in the secondary electron spectrum (see Figure 2 of
+Ref. \cite{Fasshauer14_1}). The two signals are well separated in energy
+and both consist of a main peak and a shoulder at higher kinetic energies
+of the ICD electron.
+We earlier showed a clear
+geometry dependence of peak intensity relation of the NeNe-ICD and NeAr-ICD
+and utilized this property to determine the structure of
+heteroatomic rare gas clusters \cite{Fasshauer14_1}.
+
+The peak structure of one main peak and a shoulder at higher energies has been
+discussed for the NeAr before. Theoretical investigations indicate that the
+shape might be caused by several vibrational levels of the NeAr dimer
+being involved in the decay process ($v=0,1,2$) \cite{Scheit06}. However, very
+recent experimental results of the ICD in the NeAr dimer show a symmetric peak
+without a shoulder \cite{OKeeffe14}. In order to explain this, the authors assume
+a bond contraction of the Ne$^+$Ar to happen prior to the decay.
+This nuclear rearrangement would contradict the
+theoretically predicted lifetime of the system and therefore they propose
+the prior value to be wrong and give an estimate for a higher lifetime.
+Since the shoulder appears in the spectrum of clusters only and not in the
+dimer spectra, we interpret these experimental results of the dimer to confirm our
+findings, that the shoulder stems from ICD with interaction partners of the
+next shell \cite{Fasshauer14_1}. This hypothesis is furtherly supported by the
+fact that no bound vibrational levels exist in small neon clusters and the
+shape of the peak is observed for the NeNe-ICD as well \cite{}.
+Because of the lack of eventually involved vibrational levels, we will
+focus on the NeNe-ICD part of the ICD electron spectra of the NeAr clusters
+and analyze them in more detail.
+
+%Using the simulations of
+%cluster model structures, we were able to explain the shoulders of both
+%the NeNe-ICD and the NeAr-ICD peak by decay with decay partners of the next
+%shell.
+
+%While the shoulder of the NeAr-ICD peak might be able to be explained
+%by a decay of higher vibrational levels \cite{Scheit06} bound vibrational
+%states do not exist in pure neon clusters. \cite{} 
+%Other decay processes resulting in secondary electrons of the corresponding
+%kinetic energies between \unit[2.5]{eV} and \unit[3.5]{eV} are not known.
+%Therefore, we can conclude that this shoulder stems from next shell ICD.
+%In the following, we will zoom in to the NeNe-ICD part of the spectra
+%of Figure xyz of Ref. \cite{Fasshauer14_1} and analyze them in more detail.
+
 \begin{figure}[h]
@@
           The different peak groups resemble different pair types
-          within the NeAr clusters. The lowest energy peaks (\textbf{a})
+          within the NeAr clusters. The lowest energy peaks (\textbf{(a)})
           refer to nearest neighbours
-          of different shells, the peak group \textbf{b} refers
-          to nearest neighbours within one shell and the peak group \textbf{c}
+          of different shells, the peak group \textbf{(b)} refers
+          to nearest neighbours within one shell and the peak group \textbf{(c)}
           refers to next nearest neighbours between different shells.
-          The peaks in group \textbf{d} contain both peaks stemming from
+          The other peaks contain both peaks stemming from
           pairs within the same shell as well as pairs consisting of atoms
           of different shells.}
- \label{figure:rot}
+ \label{figure:rot_blue}
 \end{figure}
 
-%\begin{figure}
-% \centering
-% \includegraphics[width=\textwidth]{pics/blue.pdf}
-% \caption{}
-% \label{figure:blue}
-%\end{figure}
+In Figure \ref{figure:rot_blue} the ICD electron spectra for the NeNe-ICD
+part of heterogeneous clusters are shown as stick spectra
+for set 3 and set 5. Hereby, we stick to the naming and the color code of
+Ref. \cite{Fasshauer14_1}. Both spectra exhibit a similar pattern of peak groups.
+The groups are found around \unit[1.0]{eV} (group \textbf{(a)}),
+around \unit[1.7]{eV} (group \textbf{(b)}), around \unit[2.6]{eV}
+(group \textbf{(c)})
+and from \unit[3]{eV} to \unit[4]{eV}. By comparing
+the interatomic distances of which these peaks originate to their occurance
+in the cluster structures, the peak groups can be assigned to atom pairs
+within the cluster. For group \textbf{(a)} the peaks stem from decays
+between two nearest neighbour atoms of two different shells,
+while group \textbf{(b)}
+stems from the decay partners being nearest neighbours in the same shell.
+Group \textbf{(c)} can be assigned to next-nearest neighbours in adjacent shells
+and the other peaks stem from a mixture of pairs which cannot unambigiously
+be categorized because different kinds of peaks intersect each other.
 
-\subsection{Icosahedral vs. fcc Structure of Clusters}
+Obviously, the peak groups have a fine structure which originates from
+different positions of the decay partners within a shell (face, egde or vertex).
+For the investigated ideal icosahedral structures,
+these pairs of group \textbf{(a)}
+are from low to high kinetic energies: vertex-vertex, edge-edge, edge-face and
+face-face. Due to vibrational broadening of the peaks the experimental observation
+of this fine structure is unlikely in neon clusters.
+
+Concluding these findings, there is not neccessarily only one kind of nearest
+neighbours in clusters. Even the next-nearest neighbours are closer to
+twice the interatomic distance of the closest pair with an open decay channel.
+Therefore, as formerly supposed, decay partners of twice the closest interatomic
+distance indeed have a very small contribution to the total spectrum. However,
+all other decay partners do have to be taken into account in order to simulate
+an ICD spectrum of clusters.
+
+\subsection{Icosahedral vs. Cuboctahedral Structure of Clusters}
+\label{sec:icofcc}
+We would like to recall that clusters with an icosahedral structure
+have shorter interatomic distances between shells than within the same
+shell.
+In terms of the ICD, different groups of nearest neighbours exist,
+one within the same shell and one
+between adjacent shells. This is characteristic for icosahedral cluster structures.
+Cuboctahedral cluster structures on the other hand are characterized by only
+one interatomic distance. 
+Therefore, icosahedral cluster structures should be distinguishable from
+cuboctahedral clusters by the number of peaks as shown in Figure
+\ref{figure:reinNe}.
+
 \begin{figure}[h]
@@
 \end{figure}
+
+Whether or not the cluster structures would be distinguishable in experiment
+will depend the vibrational broadening of the peaks, the experimental
+resolution and difference of the interatomic distances
+and hence the energy difference of the peaks in the spectrum of the
+icosahedral structure. In this proof-of-principle discussion
+we chose neon clusters for comparison with experiment but for the distinction
+of cluster structures it might be recommendable to choose atoms with larger
+internuclear distances in clusters.

### 2015-11-30 computational.tex
add corrections to entire manuscript

--- 2015-10-05 computational.tex
@@
 \section{Computational Details}
+\label{sec:computational}
+The cluster structures used were constructed to have an ideal icosahedral or
+face-centered-cubic geometry with optional additional incomplete outermost
+shells. These are based on the van der Waals radii for neon
+$r_{Ne}=\unit[1.54]{\AA}$
+and argon $r_{Ar}=\unit[1.88]{\AA}$ \cite{Bondi64}.
+In case of the NeAr clusters two of those
+cluster structures from Ref. \cite{Fasshauer14_1} that matched best
+with the combination of the argon content in the cluster,
+the NeAr-ICD to total
+ICD ratio and the peak position of the NeAr-ICD peak were used.
+These are $C_{Ar}=3$, $C_{Ne}=1$, $S_{Ne}=7$
+for set 3
+and $C_{Ar}=2$, $C_{Ne}=1$, $S_{Ne}=13$ for set 5, where $C_{Ar}$ denotes
+the edge length of the argon core, $C_{Ne}$ denotes the number of complete
+neon shells around the argon core and $S_{Ne}$ denotes the number of 
+triangular surfaces additionally covered by neon atoms.
 
-\begin{table}[!h]
+\begin{table}[h]
  \caption{Experimental values for the single ionization potentials
@@
 \end{table}
+
+The calculations to obtain the ICD electron spectra of those cluster
+structures were performed with
+the program HARDRoC \cite{HARDRoC} using experimental ionization energies shown
+in Table \ref{table:exp_input} and curves fitted to the decay width of the
+NeNe ICD of Ref. \cite{Averbukh06_1}.

### 2015-11-30 intro.tex
add corrections to entire manuscript

@@
 
-The two units $A$ and $B$ are both positively charged, repell each other and
+In the final state,
+the two units $A$ and $B$ are both positively charged, repell each other and
 thereby undergo a Coulomb explosion. This process was predicted theoretically
@@
 and proteins \cite{Harbach13}. Additionally it has given raise to
-the investigation of a whole zoo of ICD-like processes (see Ref. \cite{}
+the investigation of a whole zoo of ICD-like processes (see Ref.
+\cite{Hergenhahn11,Jahnke15}
 and references therein).
 
-In order to undergo an ICD and it to be observable, two criteria have to
+In order to undergo ICD and this process to be observable, two criteria have to
 be fulfilled: the energy and the coupling criterion. The energy criterion
-requires the energy conservation to hold. In case the doubly ionized final
-state is higher in energy than the singly ionized initial state, the ICD
+requires the energy conservation to hold. In case the energy of the
+doubly ionized final
+state is higher than the energy of the singly ionized initial state, the ICD
 is energetically forbidden. The coupling criterion requires the decay
@@
 such as radiative decay by emission of a photon or coupling to the nuclear
-degrees of freedom in molecules. The property calculated for this is the
+degrees of freedom in molecules. The corresponding property is the
 decay width $\Gamma = \frac{\hbar}{\tau}$, which is inversely proportional
@@
 We showed that decay pathways with decay partners at larger distances need to
-be included for larger systems with many decay partners for two reasons:
+be included for larger systems for two reasons:
 \begin{enumerate}
@@
        they are indistinguishable in the spectrum. Since the decay rate
-       is proportional to the number of such pairs as well as the peak
-       intensity, the peaks stemming from several pairs are favoured
+       as well as the peak intensity
+       is proportional to the number of such pairs,
+       the peaks stemming from several pairs are favoured
        compared to other ones at similar distances. Therefore, peaks
@@
        distance. A channel being closed at the distance to the most direct
-       beighbours might be open for interaction partners at slightly
+       neighbours might be open for interaction partners at slightly
        larger distances. If this particular decay channel is more efficient
@@
        the Electron Transfer Mediated Decay (ETMD3) process in mixed ArXe
-       clusters \cite{Fasshauer13,Fasshauer15_2}.
+       clusters \cite{Fasshauer13,Fasshauer16_1}.
 \end{enumerate}
 However, this feature of non-nearest neighbour ICD
-has so far not been addressed by itself.
+has so far not been addressed by itself and we will fill the gap in this
+paper.
 
-Rare gas clusters are favourable test systems for basic features both
+For a test system we choose rare gas clusters are. These are favourable
+for the investigation of basic features both
 from a theoretical and an experimental point of view. Their spherical
@@
 structure while large clusters have a cuboctahedral structure, which
-infinitely extended yields the solid state face-centered-cubic (fcc) structure.
+infinitely extended, yields the solid state face-centered-cubic (fcc) structure.
 In the solid state, every single atom is surrounded by twelve other atoms in the
 same distance. Surface atoms or even atoms at edges and vertices are rare
-compared to the number of atoms in the bulk. These atoms being surrounded
-by less than twelve atoms, are dominant in small clusters. Therefore,
-an icosahedral structure with a shorter distance between different shells and
-larger distances of atoms in the same shell, stabilizing surface atoms is
-energetically favourable in small clusters with a large surface-to-bulk ratio.
-Together with a structure change
+compared to the number of atoms in the bulk. 
+These atoms being surrounded
+However, in small clusters most atoms are surface atoms and are therefore
+surrounded by less than the optimal 12 atoms.
+In the icosahedral cluster structure the interatomic distance between different
+layers are shorter than between atoms of the same layer. 
+Therefore,
+this structure is favourable in small clusters with a large surface-to-bulk ratio.
+Together with the structure change from icosahedral to cuboctahedral
 the clusters' properties gradually change towards those of solids and
@@
 It is still unclear at which cluster size the favourable structures changes from
-an icosahedral to an fcc structure. Numbers in the range of 800--3000 atoms
-have been reported. \cite{Hartke02,Pahl08}
+an icosahedral to an cuboctahedral structure. Numbers in the range
+of 800--3000 atoms have been reported. \cite{Hartke02,Pahl08}
 We propose to use the ICD to be a possible tool to differentiate between
@@
 We will
-therefore first discuss the distance dependency of the ICD in general
-in section \ref{sec:theory} and then
+therefore first introduce the theoretical concepts in section \ref{sec:theory},
+present the computational details in section \ref{sec:computational},
+discuss the distance dependency of the ICD in general
+in section \ref{sec:partners} and then
 zoom in on the NeNe ICD part of the ICD spectra of NeAr clusters
@@
 our conclusions we propose the possibility to distinguish cluster structures
-of ideal icosahedral and fcc structures using ICD spectra in
+of ideal icosahedral and cuboctahedral structures using ICD spectra in
 section \ref{sec:icofcc}.

### 2015-11-30 partners.tex
add corrections to entire manuscript

@@
 initially ionized atoms with multiple decay partners it is necessary to
-understand the properties of the decay of a single pairof atoms. As can be seen
-from Eq. (\ref{}), the kinetic energy of the ICD electron follows an
+understand the properties of the decay of a single pair of atoms. As can be seen
+from Eqs. (\ref{equation:E_sec}) -- (\ref{equation:E_fin}),
+the kinetic energy of the ICD electron follows an
 $1/R$-behaviour shown in Figure \ref{figure:model_RE} for the case
@@
 \unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[11]{\AA} are
-not equidistant in energy difference but rather increase it for an increasing
-interatomic distance.
+not equidistant in their energy difference but rather decrease for
+an increasing interatomic distance.
 
 The corresponding decay widths $\Gamma$ depending on the interatomic
-distance are shown in figure \ref{figure:model_RGamma}. They show an
+distance are shown in Figure \ref{figure:model_RGamma}. They show an
 asymptotic $1/R^6$-behaviour such that the decay widths from an interatomic
-distance of \unit[7]{\AA} on, the peaks are too small to be seen in the
+distance of \unit[7]{\AA} on are too small to be seen in the
 figure. This means that in case of a neon dimer with an internuclear distance
@@
 partner at a distance of \unit[3]{\AA}. The energy distance to the next peak
-stimmeng from a decay with a decay partner with an internuclear distance of
+stemming from a decay with a decay partner with an internuclear distance of
 \unit[4]{\AA} is found at a \unit[1.20]{eV} higher kinetic energy and the
@@
 The energy difference between the peaks shown in Figure \ref{figure:model_EGamma}
-decreases with increasing distance of decay partners or kinetic energy
+decreases with an increasing distance of decay partners and at the same time
+the kinetic energy
 of the ICD electron. This means that for smaller interatomic distances and
 comparably low kinetic energies of the ICD electron, the spectrum has a higher
-resolution based on the interatomic distance of the decay partners.
+resolution.
 Therefore, a peak structure might be visible for the decay with nearest

### 2015-11-30 theory.tex
add corrections to entire manuscript

@@
 given by $\ket{\chi_{\beta}}$.
-This challenging description involving both bound and continuum states can
+Its challenging description involving both bound and continuum states can
 amongst others be achieved by the FanoADC-Stieltjes approach, where a

### 2015-11-30 pics/blue.tex
change peak description in red and blue clusters

@@
 \draw[thick] (axis cs:1.45,0.003) arc [radius=0.80cm,start angle=10,end angle=170];
-\node[pin={[pin distance=0.2cm]90:{\small across shells}}]
+\node[pin={[pin distance=0.2cm]90:{\small \textbf{(a)} across shells}}]
      at (axis cs:1.1,0.0038) {};
@@
 \draw[thick] (axis cs:2.00,0.0078) arc [radius=0.50cm,start angle=10,end angle=170];
-\node[pin={[pin distance=0.2cm]10:{\small same shell}}]
+\node[pin={[pin distance=0.2cm]10:{\small \textbf{(b)} same shell}}]
      at (axis cs:2.0,0.0080) {};
@@
 \draw[thick] (axis cs:2.90,0.0005) arc [radius=0.50cm,start angle=10,end angle=170];
-\node[pin={[pin distance=0.2cm]92:{\small across shells}}]
+\node[pin={[pin distance=0.2cm]92:{\small \textbf{(c)} across shells}}]
      at (axis cs:2.70,0.0010) {};

### 2015-11-30 pics/rot.tex
change peak description in red and blue clusters

@@
 \draw[thick] (axis cs:1.40,0.007) arc [radius=0.77cm,start angle=10,end angle=170];
-\node[pin={[pin distance=0.2cm]90:{\small across shells}}]
+\node[pin={[pin distance=0.2cm]90:{\small \textbf{(a)}\\ across shells}}]
      at (axis cs:1.0,0.0080) {};
@@
 \draw[thick] (axis cs:1.90,0.0120) arc [radius=0.55cm,start angle=10,end angle=170];
-\node[pin={[pin distance=0.2cm]10:{\small same shell}}]
+\node[pin={[pin distance=0.2cm]10:{\small \textbf{(b)} same shell}}]
      at (axis cs:1.9,0.0125) {};

### 2015-12-02 abstract.tex
ack, abstract, summary, smaller changes

\begin{abstract}
Interatomic Coulombic Decay (ICD) is an electronic decay process after
non-outer-valence ionization. It has been shown to occur in a multitude of small
and large systems. We discuss the effects of more than one possible decay
partner in detail using NeAr clusters and pure Ne clusters as examples.
The mostly underestimated contribution of decay with non-nearest neighbours
is highlighted.

We study the possibility to investigate the transition from
small clusters to the solid state by using the ICD electron spectra to
distinguish between icosahedral and cuboctahedral cluster structures.
\end{abstract}

### 2015-12-02 clusters.tex
ack, abstract, summary, smaller changes

@@
 \begin{tabular}{lcr}
- Ne(2s$^{-1}$) Ne &$\rightarrow$ & Ne(2p$^{-1}$) Ne(2p$^{-1}$)\\
- Ne(2s$^{-1}$) Ar &$\rightarrow$ & Ne(2p$^{-1}$) Ar(3p$^{-1}$)
+ Ne(2s$^{-1}$) + Ne &$\rightarrow$ & Ne(2p$^{-1}$) + Ne(2p$^{-1}$) + $e^-_{ICD}$\\
+ Ne(2s$^{-1}$) + Ar &$\rightarrow$ & Ne(2p$^{-1}$) + Ar(3p$^{-1}$) + $e^-_{ICD}$
 \end{tabular}
@@
 next shell \cite{Fasshauer14_1}. This hypothesis is furtherly supported by the
-fact that no bound vibrational levels exist in small neon clusters and the
-shape of the peak is observed for the NeNe-ICD as well \cite{}.
-Because of the lack of eventually involved vibrational levels, we will
-focus on the NeNe-ICD part of the ICD electron spectra of the NeAr clusters
-and analyze them in more detail.
+fact that
+in the clusters the decay rate scales approximately linearly
+with the number of nearest ineighbour decay partners.
+In other words, the lifetime of the
+singly ionized initial state is only a fraction of the dimer's lifetime and
+therefore, the nuclear motion will be even less important than in the dimer.
 
-%Using the simulations of
-%cluster model structures, we were able to explain the shoulders of both
-%the NeNe-ICD and the NeAr-ICD peak by decay with decay partners of the next
-%shell.
-
-%While the shoulder of the NeAr-ICD peak might be able to be explained
-%by a decay of higher vibrational levels \cite{Scheit06} bound vibrational
-%states do not exist in pure neon clusters. \cite{} 
-%Other decay processes resulting in secondary electrons of the corresponding
-%kinetic energies between \unit[2.5]{eV} and \unit[3.5]{eV} are not known.
-%Therefore, we can conclude that this shoulder stems from next shell ICD.
-%In the following, we will zoom in to the NeNe-ICD part of the spectra
-%of Figure xyz of Ref. \cite{Fasshauer14_1} and analyze them in more detail.
+In the neon dimer several vibrational states of the ionized initial state are
+involved in the decay. \cite{Santra00_1} However, in clusters the nuclear
+motion might not be fast enough to play a role due to the manifold of
+decay partners and the resulting shortening of the lifetime.
+In the following, we will focus on the NeNe-ICD part of the
+ICD electron spectra of the NeAr clusters and analyze them in more detail.
 
@@
 
+Two experimental ICD electron spectra of clusters
+with a mean cluster size $<N>$ between 47 and 512 atoms
+are available in the literature.
+\cite{Marburger03,Barth06_2} 
+The first experimental spectrum shows a very
+broad ICD electron peak without an unambiguously assignable peak structure,
+whereas the later results shows a main peak of ICD electrons and a smaller peak
+at slightly higher kinetic energies (at around \unit[3]{eV})
+that was not even assigned to be an ICD peak in the original work. This peak
+corresponds to the decay with non-nearest neighbours. However, a further peak
+structure is not visible.
+
 Whether or not the cluster structures would be distinguishable in experiment

### 2015-12-02 summary.tex
ack, abstract, summary, smaller changes

\section{Summary}
\label{sec:summary}

We have discussed two of the three aspects one needs to take into account
to simulate the ICD spectrum of rare gas clusters in detail. Due to the nature
of clusters, a neon atom ionized in the inner-valence will have several decay
partners at different distances. The larger the interatomic distance the higher
is the kinetic energy of the ICD electrons which will yield a multitude of
peaks in the spectrum. These are then weighted by the decay width, which
depends on the interatomic distance of the decay partners but also needs
to be scaled by the number of pairs of the same distance.
The manifold of all different decay events will then yield the spectrum.

When applying these apsects to cluster structures, one finds that not only
the nearest neighbours contribute to the spectrum, but several other decay
partners do as well. Decay partners until a distance of at least twice the
distance of the clostest decay partners should be taken into account.
In clusters with an icosahedral cluster structure this is especially important
because the smallest interatomic distance between atoms of the same and atoms
of different layers is different, but both distances are comparable.
This leads to a different number of peaks in the spectra which might help to
differentiate between clusters of icosahedral and cuboctahedral cluster structure.

### 2015-12-07 abstract.tex
find out that I can distinguish between bulk and surf atoms and its consequences

@@
 non-outer-valence ionization. It has been shown to occur in a multitude of small
-and large systems. We discuss the effects of more than one possible decay
-partner in detail using NeAr clusters and pure Ne clusters as examples.
-The mostly underestimated contribution of decay with non-nearest neighbours
-is highlighted.
+and large systems.
+The effects of more than one possible decay
+partner are discussed in detail using NeAr clusters
+and pure Ne clusters as examples.
+Hereby, the mostly underestimated contribution of decay with
+non-nearest neighbours is highlighted. In the neon atoms, the lifetime of the
+bulk atoms is found to be in excellent agreement with experiment, while the
+lifetimes of the surface atoms differ significantly. Hence, the experimental
+lifetime can not purely be explained by the effect of the number of
+neighbours.
 
-We study the possibility to investigate the transition from
+We propose the possibility to investigate the transition from
 small clusters to the solid state by using the ICD electron spectra to

### 2015-12-07 clusters.tex
find out that I can distinguish between bulk and surf atoms and its consequences

@@
 discussed for the NeAr before. Theoretical investigations indicate that the
-shape might be caused by several vibrational levels of the NeAr dimer
-being involved in the decay process ($v=0,1,2$) \cite{Scheit06}. However, very
+shape might be caused by different vibrational levels of the NeAr dimer
+($v=0,1,2$) being populated prior to the initial ionization, because
+the calculated lifetimes of the intermediate states were too short to allow
+for nuclear dynamics \cite{Scheit06}.
+There, the ratio of the population of the three vibrational levels 10:5:4
+was chosen to yield a spectrum close to the experimental spectrum of NeAr
+clusters.
+However,
 recent experimental results of the ICD in the NeAr dimer show a symmetric peak
@@
 This nuclear rearrangement would contradict the
-theoretically predicted lifetime of the system and therefore they propose
+theoretically predicted lifetime of the system and they therefore propose
 the prior value to be wrong and give an estimate for a higher lifetime.
+We would like to emphasize the possibility that mainly the vibrational
+ground state was populated at the temperatures at which the
+experiment was conducted and that the theoretically predicted lifetimes are
+correct.
 Since the shoulder appears in the spectrum of clusters only and not in the
@@
 findings, that the shoulder stems from ICD with interaction partners of the
-next shell \cite{Fasshauer14_1}. This hypothesis is furtherly supported by the
-fact that
-in the clusters the decay rate scales approximately linearly
-with the number of nearest ineighbour decay partners.
-In other words, the lifetime of the
-singly ionized initial state is only a fraction of the dimer's lifetime and
-therefore, the nuclear motion will be even less important than in the dimer.
+next shell \cite{Fasshauer14_1}.
+%This hypothesis is furtherly supported by the fact that
+%in the clusters the decay rate scales approximately linearly
+%with the number of nearest ineighbour decay partners.
+%In other words, the lifetime of the
+%singly ionized initial state is only a fraction of the dimer's lifetime and
+%therefore, the nuclear motion will be even less important than in the dimer.
 
 In the neon dimer several vibrational states of the ionized initial state are
-involved in the decay. \cite{Santra00_1} However, in clusters the nuclear
+involved in the decay. \cite{Santra00_1} It has furthermore been shown, that
+the experimentally determined lifetime of $\tau_NeNe=\unit[150\pm 50]{fs}$
+\cite{Schnorr13} is only in agreement with those theoretical lifetime
+calculations that explicitely include nuclear dynamics of the intermediate state.
+\cite{Schnorr15} However, the early lifetime measurements in neon clusters with
+a mean cluster size of $<N>=\unit[900]{atoms}$ show a lifetime of
+\unit[30]{fs} for surface atoms and \unit[6]{fs} for bulk atoms. This lifetime
+decrease is caused by the possibility to decay with several decay partners.
+Nuclear dynamics occur in the range of tens of femtoseconds in the dimer.
+Additionally, the driving force for a bond contraction after the initial
+ionization is higher in dimers than in clusters, where one bond contraction
+usually leads to several bond elongations. Therefore, we consider the influence
+of nuclear dynamics on the lifetime to be sufficiently small to be able to
+neglect them in clusters in a first description.
+\cite{Santra01_3,Ohrwall04}
+However, in clusters the nuclear
 motion might not be fast enough to play a role due to the manifold of
@@
 
-\subsection{Icosahedral vs. Cuboctahedral Structure of Clusters}
+\subsection{Neon clusters: Icosahedral vs. Cuboctahedral Structure of Clusters}
 \label{sec:icofcc}
-We would like to recall that clusters with an icosahedral structure
+We study two cluster structures of \unit[55]{atoms} each, where one has an
+idealized icosahedral and the other one has an idealized cuboctahedral structure.
+They hence consist of 13 core and 42 surface atoms each. It was predicted
+theoretically and proven experimentally that the lifetimes of ionized bulk atoms
+is shorter than of ionized surface atoms due to the smaller number of direct
+neighbours of surface atoms. The experimentally determined lifetimes are
+$\tau_{surf} = \unit[30]{fs}$ and $\tau_{bulk} = \unit[6\pm 1]{fs}$.
+For our \unit[55]{atom} cluster the decay widths and lifetimes are listed in
+Table \ref{table:lifetimes}.
+
+\begin{table}[h]
+ \centering
+ \caption{Calculated decay widths and lifetimes of bulk and surface atoms
+          for icosahedral and cuboctahedral clusters of 55 atoms.}
+ \begin{tabular}{llrr}
+  \toprule
+               &                            & $\Gamma$ [meV] & $\tau$ [fs]\\
+  \midrule
+   \multirow{2}{*}{icosahedral}   & bulk    & 125            & 5.3 \\
+                                  & surface &  67            & 9.8 \\
+  \midrule
+   \multirow{2}{*}{cuboctahedral} & bulk    & 140            & 4.7 \\
+                                  & surface &  78            & 8.4 \\
+  \bottomrule
+ \end{tabular}
+ \label{table:lifetimes}
+\end{table}
+
+For both the icosahedral and the cuboctahedral cluster structures the lifetimes
+of the bulk atoms are in excellent agreement with experiment.
+However, the theoretical lifetimes of the surface atoms are significantly
+smaller than the experimental lifetime. Let us for a moment assume that the
+experimental lifetimes are correct. Then we have to consider three error sources:
+the nuclear motion excluded in out approach, the different cluster sizes,
+a different stabilization of charges between the
+inner-valence ionized and the outer-valence ionized atom compared to the bulk.
+In small clusters, the number of face surface atoms is small compared to the
+number of edge and vertex atoms in the surface. The larger the clusters are,
+the larger is the relative number of the surface atoms. These surface atoms
+in face psoitions have more direct neighbours than atoms in vertex positions.
+Therefore, our estimated lifetime of the average surface atoms in the small
+clusters should be slightly larger than in larger clusters. A pure structure
+effect does not explain the difference between the experimental and the
+theoretical results.
+
+It remains to discuss the influence of the different charge stabilizations of
+inner- and outer-valence vacancies. The decay width is proportional to
+$\frac{1}{\omega_{vp}^4}$ where the energy of the virtual photon ($vp$) is given
+by
+
+\begin{equation}
+ \omega_{vp} = SIP(X_{in}) - SIP(X_D)   .
+\end{equation}
+
+If the stabilization difference of the inner-valence vacancy between the bulk
+and the surface atoms than the corresponding difference of the outer-valence
+vacancy, the transferred energy is increased in case of the surface atoms
+($\omega_{vp,surf} > \omega_{vp,bulk}$). As a consequence, the decay width
+is decreased and the lifetime is increased. Unfortunately, only the initial
+state energy differences are to be found in the literature \cite{Ohrwall04}.
+Hence, a validation of this cause is currently not possible.
+
+Before discussing the ICD spectra shown in Figure \ref{figure:reinNe} of
+the icosahedral and cuboctahedral cluster
+structures, we would like to recall that clusters with an icosahedral structure
 have shorter interatomic distances between shells than within the same
@@
 one within the same shell and one
-between adjacent shells. This is characteristic for icosahedral cluster structures.
-Cuboctahedral cluster structures on the other hand are characterized by only
-one interatomic distance. 
+between adjacent shells. This is characteristic for icosahedral cluster
+structures. Cuboctahedral cluster structures on the other hand are characterized
+by only one interatomic distance. 
 Therefore, icosahedral cluster structures should be distinguishable from
-cuboctahedral clusters by the number of peaks as shown in Figure
+cuboctahedral clusters by the number of peaks, which can be seen in Figure
 \ref{figure:reinNe}.
@@
 broad ICD electron peak without an unambiguously assignable peak structure,
-whereas the later results shows a main peak of ICD electrons and a smaller peak
+whereas the later results show a main peak of ICD electrons and a smaller peak
 at slightly higher kinetic energies (at around \unit[3]{eV})

### 2015-12-07 partners.tex
find out that I can distinguish between bulk and surf atoms and its consequences

@@
 seen that the kinetic energies stemming from equidistant peaks of
-\unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[11]{\AA} are
+\unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[9]{\AA} are
 not equidistant in their energy difference but rather decrease for
@@
 decay partners at distances of \unit[3]{\AA}, \unit[4]{\AA}, \dots,
-\unit[11]{\AA} shown in Figure \ref{figure:model_EGamma}. Here, the kinetic
+\unit[9]{\AA} shown in Figure \ref{figure:model_EGamma}. Here, the kinetic
 energy of the ICD electron is depicted on the abscissae while the decay
@@
  \caption{ICD electron spectrum for interaction partner distances of
-          \unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[11]{\AA}.
+          \unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[9]{\AA}.
           The energy difference between equidistant interaction partners

### 2015-12-07 summary.tex
find out that I can distinguish between bulk and surf atoms and its consequences

@@
 
-When applying these apsects to cluster structures, one finds that not only
+When applying these aspects to cluster structures, one finds that not only
 the nearest neighbours contribute to the spectrum, but several other decay
@@
 differentiate between clusters of icosahedral and cuboctahedral cluster structure.
+
+While the theoretical lifetime of the bulk atoms show an excellent agreement
+with experiment, the lifetimes of the surface atoms differ significantly.
+Assuming the experimentally determined lifetime to be correct, this deviation
+might be caused by different static cluster structures than taken into account
+in this work, by different energetic stabilization of charges or by nuclear
+dynamics. Which of these reasons explains the experiment can not be determined
+at the moment. Experimentally determined photoelectron spectra of the outer
+valence of high resolution in neon clusters would help to solve this puzzle.

### 2016-01-10 abstract.tex
changes before resubmitting OBS: no commit before minor change in intro

@@
 \begin{abstract}
-Interatomic Coulombic Decay (ICD) is an electronic decay process after
-non-outer-valence ionization. It has been shown to occur in a multitude of small
+Interatomic Coulombic Decay (ICD) is an electronic decay process of
+excited, ionized systems. It has been shown to occur in a multitude of small
 and large systems.
 The effects of more than one possible decay
-partner are discussed in detail using NeAr clusters
-and pure Ne clusters as examples.
+partner are discussed in detail illustrated by simulated ICD electron spectra
+of NeAr clusters and pure Ne clusters.
 Hereby, the mostly underestimated contribution of decay with
-non-nearest neighbours is highlighted. In the neon atoms, the lifetime of the
+non-nearest neighbours is highlighted. In the neon clusters, the lifetime of the
 bulk atoms is found to be in excellent agreement with experiment, while the

### 2016-01-10 clusters.tex
changes before resubmitting OBS: no commit before minor change in intro

@@
 involved in the decay. \cite{Santra00_1} It has furthermore been shown, that
-the experimentally determined lifetime of $\tau_NeNe=\unit[150\pm 50]{fs}$
+the experimentally determined lifetime of $\tau_{NeNe}=\unit[150\pm 50]{fs}$
 \cite{Schnorr13} is only in agreement with those theoretical lifetime
-calculations that explicitely include nuclear dynamics of the intermediate state.
+calculations that explicitly include nuclear dynamics of the intermediate state.
 \cite{Schnorr15} However, the early lifetime measurements in neon clusters with
@@
  \centering
- \includegraphics[width=\columnwidth]{pics/rot.pdf}\\
- \includegraphics[width=\columnwidth]{pics/blue.pdf}
+ \includegraphics[width=0.7\columnwidth]{pics/rot.pdf}\\
+ \includegraphics[width=0.7\columnwidth]{pics/blue.pdf}
  \caption{ICD spectra for the NeNe-ICD part of the structures of set 3 and
@@
           to nearest neighbours within one shell and the peak group \textbf{(c)}
-          refers to next nearest neighbours between different shells.
+          refers to next-nearest neighbours between adjacent shells.
           The other peaks contain both peaks stemming from
@@
 (group \textbf{(c)})
-and from \unit[3]{eV} to \unit[4]{eV}. By comparing
-the interatomic distances of which these peaks originate to their occurance
-in the cluster structures, the peak groups can be assigned to atom pairs
+and from \unit[3]{eV} to \unit[4]{eV}.
+The peak groups can be assigned to atom pairs
 within the cluster. For group \textbf{(a)} the peaks stem from decays
@@
 stems from the decay partners being nearest neighbours in the same shell.
-Group \textbf{(c)} can be assigned to next-nearest neighbours in adjacent shells
+Group \textbf{(c)} can be assigned to non-nearest neighbours in adjacent shells
 and the other peaks stem from a mixture of pairs which cannot unambigiously
@@
 twice the interatomic distance of the closest pair with an open decay channel.
-Therefore, as formerly supposed, decay partners of twice the closest interatomic
-distance indeed have a very small contribution to the total spectrum. However,
-all other decay partners do have to be taken into account in order to simulate
-an ICD spectrum of clusters.
+Therefore, also non-nearest decay partners need to be taken into account
+in order to simulate ICD spectra of clusters.
+It can be considered safe to neglect decay partners at sufficiently larger
+distances than twice the closest interatomic distance between decay partners
+with open channels.
 
@@
 is shorter than of ionized surface atoms due to the smaller number of direct
-neighbours of surface atoms. The experimentally determined lifetimes are
+neighbours of surface atoms. \cite{Santra01_3,Ohrwall04}
+The experimentally determined lifetimes are
 $\tau_{surf} = \unit[30]{fs}$ and $\tau_{bulk} = \unit[6\pm 1]{fs}$.
@@
 However, the theoretical lifetimes of the surface atoms are significantly
-smaller than the experimental lifetime. Let us for a moment assume that the
-experimental lifetimes are correct. Then we have to consider three error sources:
-the nuclear motion excluded in out approach, the different cluster sizes,
-a different stabilization of charges between the
+smaller than the experimental lifetime. Assuming that the
+experimental lifetimes are correct, we have to consider three error sources:
+1. the nuclear motion excluded in our approach, 2. the different cluster sizes,
+and 3. a different stabilization of charges between the
 inner-valence ionized and the outer-valence ionized atom compared to the bulk.
@@
 the larger is the relative number of the surface atoms. These surface atoms
-in face psoitions have more direct neighbours than atoms in vertex positions.
+in face positions have more direct neighbours than atoms in vertex positions.
 Therefore, our estimated lifetime of the average surface atoms in the small
@@
 If the stabilization difference of the inner-valence vacancy between the bulk
-and the surface atoms than the corresponding difference of the outer-valence
+and the surface atoms is larger than the corresponding difference of
+the outer-valence
 vacancy, the transferred energy is increased in case of the surface atoms
@@
 
-Before discussing the ICD spectra shown in Figure \ref{figure:reinNe} of
-the icosahedral and cuboctahedral cluster
-structures, we would like to recall that clusters with an icosahedral structure
+Before discussing the ICD spectra  of the icosahedral and cuboctahedral
+cluster structures shown in Figure \ref{figure:reinNe}, we would like to
+recall that clusters with an icosahedral structure
 have shorter interatomic distances between shells than within the same
@@
  \caption{ICD spectra of pure neon clusters consisting of 55 atoms in
-          icosahedral and fcc structure. In clusters with an ideal fcc structure
+          icosahedral and cuboctahedral structure. In clusters with an
+          ideal cuboctahedral structure
           all interatomic distances are the same and hence only one peak
@@
 that was not even assigned to be an ICD peak in the original work. This peak
-corresponds to the decay with non-nearest neighbours. However, a further peak
+corresponds to the decay with non-nearest neighbours in the adjacent shell.
+However, a further peak
 structure is not visible.
@@
 Whether or not the cluster structures would be distinguishable in experiment
-will depend the vibrational broadening of the peaks, the experimental
+will depend on the vibrational broadening of the peaks, the experimental
 resolution and difference of the interatomic distances

### 2016-01-10 computational.tex
ack, abstract, summary, smaller changes
changes before resubmitting OBS: no commit before minor change in intro

@@
 In case of the NeAr clusters two of those
-cluster structures from Ref. \cite{Fasshauer14_1} that matched best
-with the combination of the argon content in the cluster,
+cluster structures from Ref. \cite{Fasshauer14_1}, where the theoretical
+and experimental argon content in the cluster,
 the NeAr-ICD to total
-ICD ratio and the peak position of the NeAr-ICD peak were used.
-These are $C_{Ar}=3$, $C_{Ne}=1$, $S_{Ne}=7$
-for set 3
-and $C_{Ar}=2$, $C_{Ne}=1$, $S_{Ne}=13$ for set 5, where $C_{Ar}$ denotes
+ICD ratio and the peak position of the NeAr-ICD peak matched best for a given
+manifold (set) of clusters produced under certain experimental conditions,
+have been chosen.
+These are $C_{Ar}=3$, $C_{Ne}=1$, $S_{Ne}=7$ for set 3
+and $C_{Ar}=2$, $C_{Ne}=1$, $S_{Ne}=13$ for set 5 where we used the same
+nomenclature as in Ref. \cite{Fasshauer14_1}. Hence, $C_{Ar}$ denotes
 the edge length of the argon core, $C_{Ne}$ denotes the number of complete
@@
 in Table \ref{table:exp_input} and curves fitted to the decay width of the
-NeNe ICD of Ref. \cite{Averbukh06_1}.
+NeNe ICD of Ref. \cite{Averbukh06_1} and the NeAr decay widths of Ref.
+\cite{Fasshauer14_1}. These fitted curves yield lifetimes
+$\tau=\frac{\hbar}{\Gamma}$ at the corresponding equilibrium distances of
+$\tau_{NeNe}= \unit[60]{fs}$ and
+$\tau_{NeAr}= \unit[44]{fs}$.

### 2016-01-10 intro.tex
changes before resubmitting OBS: no commit before minor change in intro

@@
 The Interatomic Coulombic Decay (ICD) is an electronic decay process of an atom or
-molecule (a unit) involving atoms or molecules of the environment. After an
-ionization from the sub-valence region of a unit $A$, the vacancy is filled
-by an electron of the same unit and the excess energy is transferred to a decay
-partner $B$, which subsequently get ionized:
+molecule (a unit $A$) involving atoms or molecules of the environment. After
+creation of a sub-outer-valence vacancy in $A$, this vacancy is filled
+by an electron of the same unit and the excess energy (often called the energy of
+a virtual photon $\omega_{vp}$) is transferred to a decay
+partner $B$, which subsequently gets ionized:
 
 \begin{equation*}
- A^+ + B \rightarrow A^+ + B^+ + e^-_{ICD}  .
+ A^{*+} + B \rightarrow A^+ + B^+ + e^-_{ICD}  .
 \end{equation*}
@@
 it has been studied in a multitude of different systems such as small and large
-rare gas clusters \cite{many,Fasshauer14_1},
-clusters of small molecules \cite{},
-quantum dots \cite{Bande13}
-and proteins \cite{Harbach13}. Additionally it has given raise to
-the investigation of a whole zoo of ICD-like processes (see Ref.
+rare gas clusters \cite{Santra00_1,Santra01_1,Santra01_3,Ohrwall04,Averbukh06_1,
+Lundwall07,Jahnke10,Forstel13,Mucke15,Fasshauer14_1},
+clusters of small molecules \cite{Zobeley98,Pernpointner06,Mueller06,
+Kryzhevoi11_1,Ghosh13a},
+quantum dots \cite{Bande13}, proteins \cite{Harbach13}, it is expected
+to play a role in DNA damage in radiation therapy \cite{Alizadeh15}
+and may be used to destroy malign
+tissue \cite{Gokhberg14,Trinter14}. 
+Additionally it has given rise to
+the investigation of a manifold of ICD-like processes (see Ref.
 \cite{Hergenhahn11,Jahnke15}
@@
 the direct vicinity, because the decay widths with decay partners further away
-was considered to be negligible. Therefore, the decay was studied in clusters
-up to 13 neon atoms considering the initial ionization of only the central
-atom and not the other ones \cite{Santra01_3}. In this study, a higher than
+were considered to be negligible. Therefore, the decay was studied in clusters
+up to 13 neon atoms of equal interatomic distances considering the initial
+ionization of only the central
+atom and not the other ones \cite{Santra01_3}. The largest cluster had
+a cuboctahedral structure. In this study, a higher than
 linear dependence of the decay width on the number of neighbours was
-observed. A linear dependence would be expected for equally decay partners
+observed. A linear dependence would be expected for equal decay partners
 at equal distances from the initially ionized atom in the same environment.
@@
 
-We showed that decay pathways with decay partners at larger distances need to
+It was shown in earlier studies \cite{Fasshauer13,Fasshauer14_1,Fasshauer16_1}
+that decay pathways with decay partners at larger distances need to
 be included for larger systems for two reasons:
@@
        in ICD spectra of clusters. \cite{Fasshauer14_1}
- \item The opening of ICD-like decay channels depend on the interatomic
-       distance. A channel being closed at the distance to the most direct
+ \item The opening of ICD-like decay channels depends on the interatomic
+       distance, which is characteristic for every atom pair.
+       A channel being closed at the distance to the most direct
        neighbours might be open for interaction partners at slightly
@@
 \end{enumerate}
+
+Especially in the biological systems, in which ICD is discussed to play an
+important role \cite{Alizadeh15,Gokhberg14,Trinter14}
+the DNA is surrounded by multiple moving
+water molecules which can act as decay partners. Therefore, understanding the
+effect of non-nrearest neighbour decay will be crucial to study these systems.
 However, this feature of non-nearest neighbour ICD
@@
 
-For a test system we choose rare gas clusters are. These are favourable
+For a test system we choose rare gas clusters. These are favourable
 for the investigation of basic features both
@@
 compared to the number of atoms in the bulk. 
-These atoms being surrounded
 However, in small clusters most atoms are surface atoms and are therefore
 surrounded by less than the optimal 12 atoms.
-In the icosahedral cluster structure the interatomic distance between different
+In the icosahedral cluster structure the interatomic distances between different
 layers are shorter than between atoms of the same layer. 
@@
 conductivity as well as magnetizability can be observed. \cite{Benfield92}
-It is still unclear at which cluster size the favourable structures changes from
+It is still unclear at which cluster size the favourable structure changes from
 an icosahedral to an cuboctahedral structure. Numbers in the range
 of 800--3000 atoms have been reported. \cite{Hartke02,Pahl08}
-We propose to use the ICD to be a possible tool to differentiate between
-icosahedral and fcc cluster structures using the different distance
+We propose to use the ICD to be a possible tool to distinguish between
+icosahedral and cuboctahedral cluster structures using the different distance
 patterns in the cluster structures.
@@
 in section \ref{sec:partners} and then
-zoom in on the NeNe ICD part of the ICD spectra of NeAr clusters
+discuss the NeNe ICD part of the ICD spectra of NeAr clusters
 \cite{Fasshauer14_1} in section \ref{sec:near}. Here we will discuss the

### 2016-01-10 letters/reconsider.tex
changes before resubmitting OBS: no commit before minor change in intro

\documentclass[DIN,10pt,pagenumber=false,parskip=half,fromalign=left,fromphone=false,fromemail=true,fromurl=false,fromlogo=true,fromrule=false]{scrlttr2}
\usepackage[utf8]{inputenc}
\usepackage{ngerman}
\usepackage{units}
\usepackage{tabularx}
\usepackage[right]{eurosym}
\usepackage{graphicx}
\usepackage[top=2cm,bottom=0cm,left=2cm,right=2cm]{geometry}
%\RequirePackage{graphicx}

\setkomavar{fromname}{Dr. Elke Faßhauer}
\setkomavar{fromaddress}{CTCC\\ University of Tromsø{}
                         --- The Arctic University of Norway
                         \\ 9037 Tromsø \\ Norway}
%\setkomavar{fromphone}{06221/545220}
\setkomavar{fromemail}{elke.fasshauer@uit.no}
\setkomavar{subject}{Manuscript AK11318}
\setkomavar{signature}{Elke Faßhauer -- author of NJP-104327}
\setkomavar{fromlogo}{\includegraphics[width=3cm]{uit.pdf}}

\begin{document}

\begin{letter}{New Journal of Physics\\Editorial Board}
\textheight200mm
\opening{Dear Editor,}

I would kindly like you to reconsider your evaluation of my manuscript
NJP-104327 submitted to New Journal of Physics.

There where two critizied aspects of my manuscript: 1. it being mostly directed
towards the ICD community and 2. the topic to be subtle and not conceptually new.
First, the manuscript is directed towards the ICD community but furthermore also
to the cluster and condensed matter community and indirectly to the cancer
research community. It generalizes earlier descriptions of non-nearest neighbour
ICD which is not a subtle topic in itself which we shortly mentioned earlier
(New Journal of Physics \textbf{16}, 103026 (2014).), since it explains peaks in the spectrum the
large shoulders in the ICD spectra of clusters and intrinsically carries
information about the cluster structure.

One of the big current topics is to describe the DNA damage following an ICD in
water molecules around it. Obviously, in this setting several water molecules
at different distances are involved. Understanding the effect of non-nearest
neighbour ICD is crucial for the theoretical description of the process and the
interpretation of experimental spectra. My manuscript provides the basis for
this research.

I am convinced that my article is a valuable contribution for the readership of New Journal of Physics, highly appreciated by scientists considering Interatomic Coulombic
Decay (ICD), causations of cancer as well as
the transition from atomic and molecular clusters to the solid state and beyond.

I kindly ask you to forward my work to peer review.\\

\closing{Yours sincerely,}
\end{letter}

\end{document}

### 2016-01-10 partners.tex
changes before resubmitting OBS: no commit before minor change in intro

@@
  \caption{Kinetic energy of the ICD electron depending on the interatomic
-          distance of the two atoms involved in the decay within the
+          distance of the two atoms in an isolated pair
+          involved in the decay within the
           asymptotic approximation. The kinetic energy shows a $1/R$
@@
 seen that the kinetic energies stemming from equidistant peaks of
-\unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots ,\unit[9]{\AA} are
+\unit[3]{\AA}, \unit[4]{\AA}, \unit[5]{\AA}, \dots , \unit[9]{\AA} are
 not equidistant in their energy difference but rather decrease for
@@
 \unit[9]{\AA} shown in Figure \ref{figure:model_EGamma}. Here, the kinetic
-energy of the ICD electron is depicted on the abscissae while the decay
+energy of the ICD electron is depicted on the abscissa while the decay
 width $\Gamma$ is plotted on the ordinate. Since the decay width is proportional
-to the decay rate and hence the decay propability, these spectra can directly
+to the decay rate and hence the decay probability, these spectra can directly
 be compared to experimental ICD electron spectra.

### 2016-01-10 theory.tex
changes before resubmitting OBS: no commit before minor change in intro

@@
 
-In roder to simulate the ICD electron spectra for a given cluster structure,
-the kinetic energies of the ICD electrons $E_{ICD}$ and the corresponding decay
+In order to simulate the ICD electron spectra for a given cluster structure,
+the kinetic energies of the ICD electrons $E_{ICD}$ and the corresponding
 decay widths of all pairs have to be determined. The ICD electron energies
@@
 In the asymptotic limit, which is a reasonably good approximation for
-weakly bound systems, he initial state energy is approximated by the SIP
+weakly bound systems, the initial state energy is approximated by the SIP
 of the initially ionized unit $X_{in}$ and the final state energy can be
@@
 
-\begin{align}
+\begin{eqnarray}
  E_{ICD}^\beta &= E_{in}^\beta - E_{fin}^\beta \label{equation:E_sec}\\
@@
            \label{equation:E_fin}                . 
-\end{align}
+\end{eqnarray}
 Here, $\beta$ denotes the selected decay channel.
@@
 amongst others be achieved by the FanoADC-Stieltjes approach, where a
-subset of the $2h1p$ functions within the Algebraic Diagrammatic Construction
+subset of the  $2h1p$ (2-hole-1-particle) functions within the
+Algebraic Diagrammatic Construction
 (ADC) are used to mimic the final state function $\ket{\chi_{\beta}}$.

### 2016-01-12 letters/reconsider.tex
letter and minor changes

@@
 \setkomavar{fromemail}{elke.fasshauer@uit.no}
-\setkomavar{subject}{Manuscript AK11318}
+\setkomavar{subject}{Manuscript NJP-104327}
 \setkomavar{signature}{Elke Faßhauer -- author of NJP-104327}
@@
 
-I would kindly like you to reconsider your evaluation of my manuscript
-NJP-104327 submitted to New Journal of Physics.
+My manuscript NJP-104327 has been refereed by a single Referee, whose very
+short and negative comment lead to its rejection. As I will discuss in the
+following, all criticism of the Referee is unsubstantiated.
 
-There where two critizied aspects of my manuscript: 1. it being mostly directed
-towards the ICD community and 2. the topic to be subtle and not conceptually new.
-First, the manuscript is directed towards the ICD community but furthermore also
-to the cluster and condensed matter community and indirectly to the cancer
-research community. It generalizes earlier descriptions of non-nearest neighbour
-ICD which is not a subtle topic in itself which we shortly mentioned earlier
-(New Journal of Physics \textbf{16}, 103026 (2014).), since it explains peaks in the spectrum the
-large shoulders in the ICD spectra of clusters and intrinsically carries
-information about the cluster structure.
+The Referee critisized two aspects of my manuscript: 1. it being mostly directed
+towards the ICD community and 2. its topic being too subtle and not conceptually
+new.
+The manuscript is directed towards the ICD community, but it is also
+of interest
+to the cluster and condensed matter communities as well as indirectly to cancer
+research. The Referee's criticism 1. is therefore factually wrong.
+The generalization of the descriptions of non-nearest neighbour
+ICD is therefore not a subtle topic in itself. 
+Peaks in the ICD spectra of clusters intrinsically carry
+information about the cluster structure. This fact has not been investigated
+previously and represents an important progress in the field of ICD.
+Hence, the Referee's criticism 2. is also unsubstantiated.
 
-One of the big current topics is to describe the DNA damage following an ICD in
+One of the topics which presently attract vital attention is
+to describe the DNA damage following an ICD in
 water molecules around it. Obviously, in this setting several water molecules
@@
 neighbour ICD is crucial for the theoretical description of the process and the
-interpretation of experimental spectra. My manuscript provides the basis for
-this research.
+interpretation of experimental spectra. My manuscript provides a basis for
+this research. In order to make this more clear I added two sentences
+stating this explicitly in the introduction:\\
+\emph{Especially in the biological systems, in which ICD is discussed to play an
+important role [20,21,22]
+the DNA is surrounded by multiple moving
+water molecules which can act as decay partners. Therefore, understanding the
+effect of non-nearest neighbour decay will be crucial to study these systems.}
+However, this feature of non-nearest neighbour ICD
+has so far not been addressed by itself and we will fill the gap in this
+paper. \dots
 
-I am convinced that my article is a valuable contribution for the readership of New Journal of Physics, highly appreciated by scientists considering Interatomic Coulombic
-Decay (ICD), causations of cancer as well as
-the transition from atomic and molecular clusters to the solid state and beyond.
+I am convinced that my article is a valuable contribution for the
+readership of New Journal of Physics, highly appreciated by scientists
+considering Interatomic Coulombic Decay (ICD),
+as well as the transition from atomic and molecular clusters to the solid state
+and even the causes of cancer.
 
-I kindly ask you to forward my work to peer review.\\
+I kindly ask you to further consider my work for publication in the New
+Journal of Physics and to request another Referee's opinion.
 

### 2016-03-17 letters/reply_referee.tex
revise paper after referees

\documentclass[DIN,pagenumber=false,parskip=half,fromalign=left,fromphone=true,fromemail=true,fromurl=false,fromlogo=false,fromrule=false]{scrlttr2}
\usepackage[utf8]{inputenc}
\usepackage{ngerman}
\usepackage[english]{babel}
\usepackage{units}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage[right]{eurosym}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{braket}
\usepackage{graphicx}
%\RequirePackage{graphicx}

\setkomavar{fromname}{Dr. Elke Faßhauer}
\setkomavar{fromaddress}{Department of Chemistry\\University of Troms\o --- The Artic University of Norway\\9037 Tromsø\\Norway}
\setkomavar{fromphone}{+47 40382485}
\setkomavar{fromemail}{elke.fasshauer@uit.no}
\setkomavar{subject}{Revision of My Article No. NJP-104327}
\setkomavar{signature}{Dr. Elke Faßhauer (corresponding author)}

\begin{document}
\begin{letter}{To the Editor}

	\opening{Dear Editor,}

My paper has been reviewed by two of your Referees,
who recommended it for the publication in the
New Journal of Physics subject to minor amendments.
I am thankful for the comments made by the Referees and
respond to them below. Additionally, I took the opportunity to shorten the title.

\textbf{Referee \#2} raised the following points:

\begin{enumerate}
 \item \emph{Introduction. Page 2:
             The introduction on ICD restricts the process to the prototypical
             ICD scheme of (innervalance) ionization of a cluster. I believe
             nowadays there are many more processes within the realm of ICD,
             as RICD, shakeup-ICD etc.}\\
             Also taking into account the second comment of Referee \#1:
             \emph{ICD is not only taking place after ionization. There is
             ICD after Auger, after resonant Auger, after excitation, and more.
             ICD is generally operative in nature whenever there is sufficient
             excess electronic energy in a system to ionize a neighboring atom
             or molecule. I assume that the author wanted to be brief. I
             suggest that a general statement as above is given first and then
             the author mentions that the work here concentrates on
             ionization.}\\
             the first two paragraphs of the Introduction was changed to:\\
{\color{blue}{The Interatomic Coulombic Decay (ICD) is an electronic decay process of an atom or
molecule with a sub-outer-valence vacancy involving atoms or
molecules of the environment. The decay process is initiated by the creation
of the vacancy, which can be achieved in different ways, out of which
direct ionization, excitation, an Auger decay and radioactive decay are the
most common ones. They are connected to different members of the family
of ICD-like processes such as the Electron Transfer Mediated Decay (ETMD),
the Resonance ICD (RICD), the ICD of multiply charged species like after
an Auger decay and the classical ICD (see Ref. [1, 2]
and references therein).
In this paper the classical ICD of
a sub-outer-valence
vacancy in an atom or a molecule (a unit $A$) will be discussed. After the
creation of the vacancy in $A$, it}} is filled
by an electron of the same unit and the excess energy (often called the energy of
a virtual photon $\omega_{vp}$) is transferred to a decay
partner $B$, which subsequently gets ionized:

\begin{equation*}
 A^{*+} + B \rightarrow A^+ + B^+ + e^-_{ICD}  .
\end{equation*}

In the final state,
the two units $A$ and $B$ are both positively charged, repell each other and
thereby undergo a Coulomb explosion. This process was predicted theoretically
[3], {\color{blue}{later
the first experimental evidence was found in
[4, 5] and the experimental prove was given by Jahnke et al.
[6]. Since then
it has been studied in a multitude of different systems such as small and large
rare gas clusters [7, 8, 9, 10, 11, 12, 13, 14, 15],}}
clusters of small molecules [16, 17, 18, 19, 20],
quantum dots [21], proteins [22], it is expected
to play a role in DNA damage in radiation therapy [23]
and may be used to destroy malign tissue [24, 25].

 \item \emph{It is stated, that the existence of ICD was proven in [2]. The reference is typically such, that first evidence was found in [2], the prove was given by Jahnke et al. Phys. Rev. Lett. 93, 163401. Reference [6] is typically cited, as well, as one of the experiments that showed the occurence of ICD for the first time.}\\
I changed the citation, see point 1.

 \item \emph{``The energy criterion requires energy conservation to hold'' is a somewhat strange way to describe the fact that ``a decay can only happen if the energy suffices''}\\
       The sentence was changed to:\\
       The energy criterion {\color{blue}{is a rephrasing of the energy
       conservation stating that a decay can only
       happen if the energy suffices.}}

\item \emph{Maybe ``the decay widths ... were considered to be negligible'' should be changed into something like ``decays with partner further away were considered negligible due to their decay width''.}\\
       The sentence was changed accordingly.

\item \emph{Who is we in a single author paper? (I am aware, that I sounds very strange in a scientific publication, but maybe the according sentences can be amended in order to avoid we or I.}\\
      The formulations were kept using ``we'', because a rephrasing to passive
      voice would have made the sentence overcomplicated and compromized
      comprehensibility.

\item \emph{``..the gaseous state of their components allows for a convenient cleaning... higher count rates and therefore higher resolution..'': I do not understand this sentence and I am not sure it is actually right. Maybe an experimental collaborator can help here. (Maybe it is already enough to state, that in an experiment it helps, as well, to have a homogenous, and easily controlable target.)}
      The sentence was changed to:\\
      Their spherical
symmetry and their very localized orbitals allow for an comparably easy
theoretical description of the decay processes.
{\color{blue}{The experimental techniques to produce rare gas clusters
are well established
via variety of experimental and theoretical studies
[29, 30, 31, 5]. This makes these clusters a convenient target with controlled and predictable cluster conditions available at sufficient target densities for extended time periods as required in the here described experiments.}}

\item \emph{The Van der Waals radii do not have units.}\\
      The units were added.

\item \emph{I suggest to add horizontal lines for the different internuclear distances, as that way the statement of a decreasing energy difference for larger distances becomes clear at first glance.}\\
      The horizontal lines were added to the figure.

\item \emph{I am afraid I do not understand the last two sentences of the paragraph prior to section 5. Maybe the author can rephrase them?}\\
      The sentences were changed to:\\
      This means that for small interatomic distances and
comparably low kinetic energies of the ICD electron, the
{\color{blue}{energy}} spectrum
has a higher resolution {\color{blue}{of the interatomic distances}}.
Therefore, a peak structure might be visible for the decay with nearest
neighbours (or the closest atoms with energetically allowed decay channels)
but not necessarily for all different kinds of interaction partners at larger
distances.
\end{enumerate}

\textbf{Referee \#1} raised the following points:

\begin{enumerate}
 \item \emph{Abstract. Agreement and disagreement with experiment is addressed. Which experiment? That in [6] or that in [12]? The clusters in [12] do not correspond to those addressed here. The clusters in [6] are very large compared to the one studied here and I wonder about the comparison and the conclusion drawn (see also below).}\\
       The experiment in the former Ref. [6]. The citation was explicitly added to the
       abstract. The paper now also contains the discussion the lifetimes
       in larger clusters (see below) and the statement of the abstract is still valid.
       Therefore no further changes were applied.

 \item See comment 1 of Referee \#2.
 \item \emph{The author writes: “It was shown in earlier studies [25, 12, 26] that decay pathways with decay partners at larger distances need to be included...”. I suggest that the works by Kryzhevoi on ICD in He droplets are mentioned here too.}\\
       The additional reference was added.

 \item \emph{Page 5. The 1/R6 behavior of the decay rates is mentioned and employed. The author should mention that at distances shorter than asymptotic the rates can be substantially larger (see, e.g., the case of Ne..Mg). In rare gases the 1/R6 behavior is probably adequate (are there calculations of $\Gamma$ as a function of R for a rare gas dimer like Ne..Ne ?).}\\
       The \emph{asymptotic} $1/R^6$-behaviour is mentioned to discuss the
       behaviour at large distances. However, as mentioned in the computational
       details, this approximation is not employed in this work. Instead, a
       fit to the respective computed decay width is used. Therefore, no
       changes were applied.

 \item \emph{Page 9. The author writes: “Therefore, we consider the influence of nuclear dynamics on the lifetime to be sufficiently small to be able to neglect them in clusters in a first description. [5, 6] However, in
clusters the nuclear motion might not be fast enough to play...”. The “However” is unclear. Both sentences actually say the same.}\\
       The second sentence starting with \emph{However, } was removed.

 \item \emph{Page 5. The author takes recourse to “set 3” and “set 5”. What are these sets? It cannot be expected that the reader should search in ref. [12] to find out what is meant here. Some explanatory text is needed.}\\
       The explanatory text is already part of the manuscript and to be found
       in the sentence the Referee is referring to and the following sentence.
       Therefore, no changes were applied.

 \item \emph{Figs. 4 and 5. The author should explain in simple words how these spectra were obtained. E.g., was it assumed that each atom in the cluster is initially inner-valence ionized with the same probability?}\\
       The results were obtained with the pairwise approximation, which treats
       all pairs with the same distance in the same way. This holds for every
       calculation and therefore, to make this more clear, the computational
       details were changed accordingly and now read:\\
The calculations to obtain the ICD electron spectra of all cluster
structures were performed with
the program HARDRoC [42]
{\color{blue}{based on the decomposition of the cluster into
pairs. Every pair with the same distance is treated equally. This includes the
assumption that every neon atom is ionized with the same probability.}}
It uses experimental ionization energies shown
in Table 1 and curves fitted to the decay width of the
NeNe ICD of Ref. [10] and the NeAr decay widths of Ref.
[15]. These fitted curves yield lifetimes
$\tau=\frac{\hbar}{\Gamma}$ at the corresponding equilibrium distances of         
$\tau_{NeNe}= \unit[60]{fs}$ and                                    
$\tau_{NeAr}= \unit[44]{fs}$.

 \item \emph{Fig. 4. In the experiments ([12]) the peak at around 3 eV is well seen, while here it is there but not too intense. Can this be explained?}\\
       Yes, it can be explained. Around 3 eV many minor peaks are to be found which
       are very close in energy. Folding the spectrum adds all these contributions
       up and they appear as a peak or shoulder. The caption of Fig. 4 was
       therefore appended by:\\
          In this representation the contribution of the
          peaks around \unit[3]{eV} is easily underestimated. After folding the
          spectrum with many close lying small peaks they will add up to yield
          a visible peak or shoulder (compare Ref. [15]).

 \item \emph{Will a similar explanation make the visibility of the respective peak in Fig. 5 visible in experiment?}\\
       It is visible in the experiment, which is discussed in the text. To illustrate
       it I add a figure from \emph{Chem. Phys.} \textbf{329}, 246 (2006) with
       the non-nearest neighbour ICD highlighted in blue:
       \begin{center}
        \includegraphics[]{../pics/exp_Ne_coinc_spec.png}
       \end{center}
       The larger the clusters are, the more pronounced the shoulder will be.
       In order to make the shoulder in Fig. 5 better visible, the spectra have
       been folded and incorporated in Fig. 5.

 \item \emph{I suggest to add a nice picture of the two ideal Ne clusters studied.}\\
       The pictures were added.

 \item \emph{Is the geometry of the ideal clusters optimized? Will an optimization change the picture?}\\
       The geometries of the idealized clusters presented are not optimized.
       After optimization of the structures with a force field, the distance pattern
       changed while the overall structure remained. In case of the cuboctahedral cluster
       the nearest neighbours were no longer described by only one distance but by
       different distances that are very close to the original one. In case of the
       icosahedral structure the distance pattern was split into a few characteristic
       distances, which are wider spread than in case of the cuboctahedral cluster.
       Therefore that statement that the underlying cluster structure might be
       determined by the number of peaks or without a high resolution by the width
       of the peak (the width of the icosahedral structure is larger) is unaffected.

 \item \emph{Page 12. “Two experimental ICD electron spectra of clusters with a mean cluster size < N > between 47 and 512 atoms are available...”. What does the word “between” mean here?}\\
       The spectra have been measured for mean cluster sizes between these two
       numbers. However, they were only displayed in the literature for $<N>=70$
       and $<N>=209$. Therefore, the sentence was changed to:\\
       Two experimental ICD electron spectra of clusters
       with a mean cluster size $<N>$ {\color{blue}{of 70 and 209}} atoms
       are available in the literature.
       [4, 48]

 \item \emph{Page 11. “The experimentally determined lifetimes are ...”. It is misleading to compare these experimental values with those computed for the 55 atom clusters without further discussion, like directly mentioning the size of the cluster in experiment. The whole discussion on pages 11/12 will benefit from a somewhat more coherent rewriting. I also think that if the clusters used in experiment are large and a bit unstructured (I mean that the cluster is not in its ground state structure; what was the temperature?), then there might be many atoms on the surface which may have fewer neighbors than in an idealized structure. This may also lead to longer ICD lifetimes for some of the surface atoms. May even be that the distance between atoms on the surface is different (larger) than in the bulk (?). I agree that the issue is not simple.}\\
       The experimentally investigated clusters have a mean cluster size of 900
       atoms. Therefore, I simulated the decay widths /lifetimes for clusters
       consisting of 923 atoms and added the results to the discussion.
       As expected and discussed in first manuscript, the lifetimes of the bulk
       atoms are hardly affected by the cluster size while the lifetimes of the
       surface atoms is shorter for the larger clusters. The temperature might
       indeed lead to different cluster structures. It's quantification will be
       left as a subject to future work.
       The lifetime discussion now reads:\\
{\color{blue}{We study two cluster structures,
where one has an
idealized icosahedral and the other one has an idealized cuboctahedral structure
for clusters of both \unit[55]{atoms} and \unit[923]{atoms}.
They hence consist of 13 (561) core and 42 (362) surface atoms. It was predicted
theoretically and proven experimentally that the lifetimes of ionized bulk atoms
is shorter than of ionized surface atoms due to the smaller number of direct
neighbours of surface atoms. [9, 5]
The experimentally determined lifetimes are
$\tau_{surf} = \unit[30]{fs}$ and $\tau_{bulk} = \unit[6\pm 1]{fs}$.
For our \unit[55]{atom} and \unit[923]{atom} cluster the decay widths and lifetimes
are listed in Table 2.

%\begin{table}[h]
% \centering
% \caption{Calculated decay widths and lifetimes of bulk and surface atoms
%          for icosahedral and cuboctahedral clusters of 55 and 923 atoms.}
% \begin{tabular}{llrrr}
%  \toprule
%               &                            & atoms & $\Gamma$ [meV] & $\tau$ [fs]\\
%  \midrule
%   \multirow{4}{*}{icosahedral}   & bulk    &   55  &   125          & 5.3 \\
%                                  & surface &   55  &    67          & 9.8 \\
%                                  & bulk    &  923  &   126          & 5.2 \\
%                                  & surface &  923  &    81          & 8.1 \\
%  \midrule
%   \multirow{4}{*}{cuboctahedral} & bulk    &   55  &   140          & 4.7 \\
%                                  & surface &   55  &    78          & 8.4 \\
%                                  & bulk    &  923  &   147          & 4.5 \\
%                                  & surface &  923  &    95          & 7.0 \\
%  \bottomrule
% \end{tabular}
% \label{table:lifetimes}
%\end{table}

In all cases, our results confirm the shorter lifetimes of the bulk atoms compared
to the surface atoms. Both for the icosahedral and for the cuboctahedral cluster
structure the lifetime of the bulk atoms is almost independent of the cluster size
and the difference is maximum \unit[0.2]{fs}. This can be explained by the very
similar environments of bulk atoms in smaller and larger clusters.}}
The lifetimes of the surface atoms however are smaller for the larger cluster sizes.
In small clusters, the number of face surface atoms is small compared to the
number of edge and vertex atoms in the surface. The larger the clusters are,
the larger is the relative number of the surface atoms. These surface atoms
in face positions have more direct neighbours than atoms in vertex positions.
Therefore, our estimated lifetime of the average surface atoms in the small       
clusters should be slightly larger than in larger clusters.

For both the icosahedral and the cuboctahedral cluster structures the lifetimes
of the bulk atoms are in excellent agreement with experiment.
However, the theoretical lifetimes of the surface atoms are significantly
smaller than the experimental lifetime. Assuming that the
experimental lifetimes are correct, we have to consider three error sources:      
1. the nuclear motion excluded in our approach, 2. different cluster structures,  
and 3. a different stabilization of charges between the             
inner-valence ionized and the outer-valence ionized atom compared to the bulk.

{\color{blue}{
Cluster structures with larger interatomic distances of the surface atoms between 
each other and the core atoms would explain the higher experimental lifetimes of  
the surface atoms. These could be caused by non-ideal structures due to the       
clusters' temperature.}} ...

 \item \emph{I wonder what happens in a relatively big idealized cluster if one computes the influence of all neighbors (like done in the He droplets)? If the distances are optimized? After all, there will then be very many contributors and as the Coulomb repulsion falls off ‘rapidly’ with distance, the energy of the ICD electron will not spread too much. The number of neighbors on a sphere of Radius R from a given atom grows as R2 and the rate falls as 1/R6 implying that the total fall off is only as 1/R4. Can this explain the question in point 8 above?}\\
      Throughout the entire work, the decay widths were simulated using the decay
      with all possible decay partners.
      ICD electron spectra of large neon clusters (8217 atoms) were
      calculated and the spectrum does
      hardly change qualitatively compared to the spectra of 55 atoms. ICD electrons
      at higher energies up to \unit[5.37]{eV} are observed with a low probability and the
      contribution of the decay with nonnearest neighbours is slightly increased.

      To explain the decrease of the decay by an $R^{-4}$-behaviour is an interesting
      ansatz. However, it oversimplifies the problem.
      The surface of the sphere is proportional to $R^2$, but on this surface several
      3D objects have to be placed, which in addition have the projection of a circle.
      Therefore, it is impossible to cover the entire surface of the sphere and
      the number of atoms per shell is smaller than a $R^2$-behaviour would suggest.
      It is though
      proportional to the square of the number of atoms per edge $c$
      (which can be used as an alternative measure of $R$) of the respective
      outermost shell. The number of the outermost
      shell ($os$) of a cluster with edge length $c$ can be established from 
      the total number of atoms per cluster

      \begin{equation*}
       n_{atoms,total} = \frac{10}{3} c^3 - 5 c^2 + \frac{11}{3} c -1 .
      \end{equation*}

      The number of atoms in the outermost shell is then given by
      \begin{align*}
       n_{os} &= n(c) - n(c-1)\\
              &= 10 c^2 - 20c + 12 .
      \end{align*}

      Additionally, both the icosahedral and the cuboctahedral clusters are not
      perfect spheres. This also means that, except for the first shell,
      atoms in the same shell, depending on the
      character of their position, have different distances to the central atom and
      hence correspond to different peaks in the spectrum.

      In order to illustrate this,
      please find a calculated spectrum of an excited central neon atom in cuboctahedral
      neon cluster with 14 atoms per edge (8217 atoms in total) plotted in a logarithmic
      scale:

      \begin{center}
       \includegraphics[width=0.7\textwidth]{../pics/center.pdf}
      \end{center}
      The first peak corresponds to decay partners in the first shell, but the
      next three peaks correspond to the second shell, the next five to the third
      shell etc. The further the shell is away, the more it is split into
      different distances. This makes a fit to the above equation unreasonable.

      Another feature of clusters is visible in this spectrum: the non-infinite
      dimension of clusters. The spectrum ends at \unit[5.19]{eV}, which would not occur
      in a solid state environment. However, these decays with partners at distances
      above \unit[80]{\AA} would be highly unlikely.

      This discussion holds for the optimized structures as well.

\end{enumerate}

I took the opportunity to shorten the title in order to not highlight only
one out of several aspects. It now reads:\\
      Non-nearest Neighbour ICD in 
      Clusters

        \closing{Sincerely yours,}
	\end{letter}

\end{document}

### 2016-03-17 clusters.tex
revise paper after referees

@@
 \cite{Santra01_3,Ohrwall04}
-However, in clusters the nuclear
-motion might not be fast enough to play a role due to the manifold of
-decay partners and the resulting shortening of the lifetime.
+%However, in clusters the nuclear
+%motion might not be fast enough to play a role due to the manifold of
+%decay partners and the resulting shortening of the lifetime.
 In the following, we will focus on the NeNe-ICD part of the
@@
           pairs within the same shell as well as pairs consisting of atoms
-          of different shells.}
+          of different shells. In this representation the contribution of the
+          peaks around \unit[3]{eV} is easily underestimated. After folding the
+          spectrum with many close lying small peaks they will add up to yield
+          a visible peak or shoulder (compare Ref. \cite{Fasshauer14_1}).}
  \label{figure:rot_blue}
@@
 \label{sec:icofcc}
-We study two cluster structures of \unit[55]{atoms} each, where one has an
-idealized icosahedral and the other one has an idealized cuboctahedral structure.
-They hence consist of 13 core and 42 surface atoms each. It was predicted
+We study two cluster structures (shown in Figure \ref{figure:Ne_clusters}),
+where one has an
+idealized icosahedral and the other one has an idealized cuboctahedral structure
+for clusters of both \unit[55]{atoms} and \unit[923]{atoms}.
+They hence consist of 13 (561) core and 42 (362) surface atoms.
+
+\begin{figure}[h]
+ \centering
+ \includegraphics[height=4cm]{pics/fcc.png}
+ \hspace{2cm}
+ \includegraphics[height=4cm]{pics/ico.png}
+ \caption{Cluster structures of the \unit[55]{atom} Ne clusters with
+          cuboctahedral structure (left) and icosahedral structure (right).}
+ \label{figure:Ne_clusters}
+\end{figure}
+
+It was predicted
 theoretically and proven experimentally that the lifetimes of ionized bulk atoms
@@
 $\tau_{surf} = \unit[30]{fs}$ and $\tau_{bulk} = \unit[6\pm 1]{fs}$.
-For our \unit[55]{atom} cluster the decay widths and lifetimes are listed in
-Table \ref{table:lifetimes}.
+\cite{Ohrwall04}
+For our \unit[55]{atom} and \unit[923]{atom} cluster the decay widths and lifetimes
+are listed in Table \ref{table:lifetimes}.
 
@@
  \caption{Calculated decay widths and lifetimes of bulk and surface atoms
-          for icosahedral and cuboctahedral clusters of 55 atoms.}
- \begin{tabular}{llrr}
+          for icosahedral and cuboctahedral clusters of 55 and 923 atoms.}
+ \begin{tabular}{llrrr}
   \toprule
-               &                            & $\Gamma$ [meV] & $\tau$ [fs]\\
+               &                            & atoms & $\Gamma$ [meV] & $\tau$ [fs]\\
   \midrule
-   \multirow{2}{*}{icosahedral}   & bulk    & 125            & 5.3 \\
-                                  & surface &  67            & 9.8 \\
+   \multirow{4}{*}{icosahedral}   & bulk    &   55  &   125          & 5.3 \\
+                                  & surface &   55  &    67          & 9.8 \\
+                                  & bulk    &  923  &   126          & 5.2 \\
+                                  & surface &  923  &    81          & 8.1 \\
   \midrule
-   \multirow{2}{*}{cuboctahedral} & bulk    & 140            & 4.7 \\
-                                  & surface &  78            & 8.4 \\
+   \multirow{4}{*}{cuboctahedral} & bulk    &   55  &   140          & 4.7 \\
+                                  & surface &   55  &    78          & 8.4 \\
+                                  & bulk    &  923  &   147          & 4.5 \\
+                                  & surface &  923  &    95          & 7.0 \\
   \bottomrule
@@
 \end{table}
+
+In all cases, our results confirm the shorter lifetimes of the bulk atoms compared
+to the surface atoms. Both for the icosahedral and for the cuboctahedral cluster
+structure the lifetime of the bulk atoms is almost independent of the cluster size
+and the difference is maximum \unit[0.2]{fs}. This can be explained by the very
+similar environments of bulk atoms in smaller and larger clusters.
+The lifetimes of the surface atoms however are smaller for the larger cluster sizes.
+In small clusters, the number of face surface atoms is small compared to the
+number of edge and vertex atoms in the surface. The larger the clusters are,
+the larger is the relative number of the surface atoms. These surface atoms
+in face positions have more direct neighbours than atoms in vertex positions.
+Therefore, our estimated lifetime of the average surface atoms in the small
+clusters should be slightly larger than in larger clusters.
 
@@
 experimental lifetimes are correct, we have to consider three error sources:
-1. the nuclear motion excluded in our approach, 2. the different cluster sizes,
+1. the nuclear motion excluded in our approach, 2. different cluster structures,
 and 3. a different stabilization of charges between the
 inner-valence ionized and the outer-valence ionized atom compared to the bulk.
-In small clusters, the number of face surface atoms is small compared to the
-number of edge and vertex atoms in the surface. The larger the clusters are,
-the larger is the relative number of the surface atoms. These surface atoms
-in face positions have more direct neighbours than atoms in vertex positions.
-Therefore, our estimated lifetime of the average surface atoms in the small
-clusters should be slightly larger than in larger clusters. A pure structure
-effect does not explain the difference between the experimental and the
-theoretical results.
+
+Cluster structures with larger interatomic distances of the surface atoms between
+each other and the core atoms would explain the higher experimental lifetimes of
+the surface atoms. These could be caused by non-ideal structures due to the
+clusters' temperature.
 
@@
 Two experimental ICD electron spectra of clusters
-with a mean cluster size $<N>$ between 47 and 512 atoms
+with a mean cluster size $<N>$ of 70 and 209 atoms
 are available in the literature.
 \cite{Marburger03,Barth06_2} 
-The first experimental spectrum shows a very
+The first experimental spectrum for clusters with $<N>=70$ shows a very
 broad ICD electron peak without an unambiguously assignable peak structure,

### 2016-03-17 intro.tex
letter and minor changes
revise paper after referees

@@
 The Interatomic Coulombic Decay (ICD) is an electronic decay process of an atom or
-molecule (a unit $A$) involving atoms or molecules of the environment. After
-creation of a sub-outer-valence vacancy in $A$, this vacancy is filled
+molecule with a sub-outer-valence vacancy involving atoms or
+molecules of the environment. The decay process is initiated by the creation
+of the vacancy, which can be achieved in different ways, out of which
+direct ionization, excitation, an Auger decay and radioactive decay are the
+most common ones. They are connected to different members of the family
+of ICD-like processes such as the Electron Transfer Mediated Decay (ETMD),
+the Resonance ICD (RICD), the ICD of multiply charged species like after
+an Auger decay and the classical ICD (see Ref. \cite{Hergenhahn11,Jahnke15}
+and references therein).
+In this paper the classical ICD of
+a sub-outer-valence
+vacancy in an atom or a molecule (a unit $A$) will be discussed. After
+creation of the vacancy in $A$, it is filled
 by an electron of the same unit and the excess energy (often called the energy of
@@
 thereby undergo a Coulomb explosion. This process was predicted theoretically
-\cite{Cederbaum97} and later proven experimentally \cite{Marburger03}. Since then
+\cite{Cederbaum97}, later the first experimental evidence was found in
+\cite{Marburger03,Ohrwall04} and the experimental prove was given by Jahnke et al.
+\cite{Jahnke04}. Since then
 it has been studied in a multitude of different systems such as small and large
-rare gas clusters \cite{Santra00_1,Santra01_1,Santra01_3,Ohrwall04,Averbukh06_1,
+rare gas clusters \cite{Santra00_1,Santra01_1,Santra01_3,Averbukh06_1,
 Lundwall07,Jahnke10,Forstel13,Mucke15,Fasshauer14_1},
@@
 tissue \cite{Gokhberg14,Trinter14}.
-Additionally it has given rise to
-the investigation of a manifold of ICD-like processes (see Ref.
-\cite{Hergenhahn11,Jahnke15}
-and references therein).
 
@@
 be fulfilled: the energy and the coupling criterion. The energy criterion
-requires the energy conservation to hold. In case the energy of the
+is a rephrasing of the energy conservation stating that a decay can only
+happen if the energy suffices. In case the energy of the
 doubly ionized final
@@
 The ICD process was so far mostly discussed for the case of decay partners in
-the direct vicinity, because the decay widths with decay partners further away
-were considered to be negligible. Therefore, the decay was studied in clusters
+the direct vicinity, because the decay with decay partners further away
+were considered to be negligible due to their decay width.
+Therefore, the decay was studied in clusters
 up to 13 neon atoms of equal interatomic distances considering the initial
@@
 
-It was shown in earlier studies \cite{Fasshauer13,Fasshauer14_1,Fasshauer16_1}
+It was shown in earlier studies
+\cite{kryzhevoi2007,Fasshauer13,Fasshauer14_1,Fasshauer16_1}
 that decay pathways with decay partners at larger distances need to
@@
 water molecules which can act as decay partners. Therefore, understanding the
-effect of non-nrearest neighbour decay will be crucial to study these systems.
+effect of non-nearest neighbour decay will be crucial to study these systems.
 However, this feature of non-nearest neighbour ICD
@@
 symmetry and their very localized orbitals allow for an comparably easy
-theoretical description of the decay processes and the gaseous state
-of their components allows for a convenient cleaning of the experimental
-setup allowing for higher count rates and therefore a higher resolution
-of the spectra. At the same time, the structure of the clusters reveals an
+theoretical description of the decay processes.
+The experimental techniques to produce rare gas clusters are well established
+via variety of experimental and theoretical studies
+\cite{Hagena72,Hagena81,Hagena87,Ohrwall04}.
+This makes these clusters a convenient target with controlled and predictable cluster conditions available at sufficient target densities for extended time periods as required in the here described experiments.
+At the same time, the structure of the clusters reveals an
 interesting matter of research. Small, ideal clusters exhibit an icosahedral

### 2016-03-17 partners.tex
revise paper after referees

@@
 the kinetic energy
-of the ICD electron. This means that for smaller interatomic distances and
-comparably low kinetic energies of the ICD electron, the spectrum has a higher
-resolution.
+of the ICD electron. This means that for small interatomic distances and
+comparably low kinetic energies of the ICD electron, the energy spectrum
+has a higher resolution of the interatomic distances.
 Therefore, a peak structure might be visible for the decay with nearest

### 2016-03-17 revised/NJP_master.tex
format of the paper - prepare submission

%\documentclass[aps,amssymb,preprint,a4paper,dvips]{revtex4}
\documentclass[12pt,twocolumn]{iopart}

%\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{braket}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{placeins}
%\usepackage{amsmath,amsfonts,amssymb}
\usepackage{iopams}
\usepackage{dsfont}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{units}
%\usepackage{natbib}

%Finde die Bilder
%\graphicspath{{./pics/}}

% Alphabetic counting in footnotes
\renewcommand{\thefootnote}{\alph{footnote}}

% Captions over full width

%\usepackage{caption}
%\captionsetup[figure]{format=plain, justification=raggedright, singlelinecheck=false, font=footnotesize, labelfont=bf}
%\captionsetup[table]{position=top, format=plain, justification=raggedright, singlelinecheck=false, font=footnotesize, labelfont=bf}

\begin{document}

\setlength{\tabcolsep}{12pt}

% Define some colour
\definecolor{diplom1}{rgb}{0.0 0.4 1.0}
\definecolor{diplom2}{rgb}{0.0 0.0 0.6}
\definecolor{diplom3}{RGB}{153,0,0} %unirot

%\title[Non-nearest Neighbour ICD in Clusters]{Non-nearest Neighbour ICD in Clusters: A Way to Distinguish Icosahedral
%       and Cuboctahedral Clusters?}
\title[Non-nearest Neighbour ICD in Clusters]{Non-nearest Neighbour ICD in
       Clusters}

\author{E Fasshauer}
\address{Centre for Theoretical and Computational Chemistry,
         Department of Chemistry, University of Troms\o,
         -- The Arctic University of Norway, N-9037 Troms\o, Norway}

\eads{\mailto{elke.fasshauer@uit.no}}

\date{\today}

\begin{abstract}
 \input{abstract}
\end{abstract}

\pacs{33.50.Hv, 33.70.Fd, 33.70.Jg, 34.80.Dp, 36.40.-c, 36.40.Mr}
\submitto{New Journal of Physics}

\maketitle

\input{intro}
\input{theory}
\input{computational}
\input{partners}
\input{clusters}
\input{summary}

\input{ack}

\eject
\section*{References}
%\bibliographystyle{unsrt}
%\bibliography{theolit}

\begin{thebibliography}{10}

\bibitem{Hergenhahn11}
U.~Hergenhahn.
\newblock {Interatomic and Intermolecular Coulombic Decay: The Early Years}.
\newblock {\em J. Electron Spectrosc. Relat. Phenom.}, 184:78, 2011.

\bibitem{Jahnke15}
T.~Jahnke.
\newblock {Interatomic and intermolecular Coulombic decay: the coming of age
  story}.
\newblock {\em J. Phys. B: Atomic, Molecular and Optical Physics}, 48:082001,
  2015.

\bibitem{Cederbaum97}
L.~S. Cederbaum, J.~Zobeley, and F.~Tarantelli.
\newblock {Giant Intermolecular Decay and Fragmentation of Clusters}.
\newblock {\em Phys. Rev. Lett.}, 79(24):4778, 1997.

\bibitem{Marburger03}
S.~Marburger, O.~Kugeler, U.~Hergenhahn, and T.~M{\"o}ller.
\newblock Experimental evidence for interatomic coulombic decay in ne clusters.
\newblock {\em Phys. Rev. Lett.}, 90(20):203401, 2003.

\bibitem{Ohrwall04}
G.~{\"O}hrwall, M.~Tchaplyguine, M.~Lundwall, R.~Feifel, H.~Bergersen,
  T.~Rander, A.~Lindblad, J.~Schulz, S.~Peredkov, S.~Barth, S.~Marburger,
  U.~Hergenhahn, S.~Svensson, and O.~Bj{\"o}rneholm.
\newblock {Femtosecond Interatomic Coulombic Decay in Free Neon Clusters: Large
  Lifetime Differences between Surface and Bulk}.
\newblock {\em Phys. Rev. Lett.}, 93(17):173401, 2004.

\bibitem{Jahnke04}
T.~Jahnke, A.~Czasch, M.~S. Sch{\"o}ffler, S.~Sch{\"o}ssler, A.~Knapp,
  M.~K{\"a}sz, J.~Titze, C.~Wimmer, K.~Kreidi, R.~E. Grisenti, A.~Staudte,
  O.~Jagutzki, U.~Hergenhahn, H.~Schmidt-B{\"o}cking, and R.~D{\"o}rner.
\newblock Experimental observation of interatomic coulombic decay in neon
  dimers.
\newblock {\em Phys. Rev. Lett.}, 93(16):163401, 2004.

\bibitem{Santra00_1}
R.~Santra, J.~Zobeley, L.~S. Cederbaum, and N.~Moiseyev.
\newblock {Interatomic Coulombic Decay in van der Waals Clusters and Impact of
  Nuclear Motion}.
\newblock {\em Phys. Rev. Lett.}, 85:4490, 2000.

\bibitem{Santra01_1}
R.~Santra, J.~Zobeley, L.~S. Cederbaum, and F.~Tarantelli.
\newblock {Intermolecular Coulombic decay of clusters}.
\newblock {\em J. Electron Spectrosc. Relat. Phenom.}, 114--116:41, 2001.

\bibitem{Santra01_3}
R.~Santra, J.~Zobeley, and L.~S. Cederbaum.
\newblock {Electronic decay of valence holes in clusters and condensed matter}.
\newblock {\em Phys. Rev. B}, 64(24):245104, 2001.

\bibitem{Averbukh06_1}
V.~Averbukh and L.~S. Cederbaum.
\newblock {Calculation of interatomic decay widths of vacancy states
  delocalized due to inversion symmetry}.
\newblock {\em J. Chem. Phys.}, 125:094107, 2006.

\bibitem{Lundwall07}
M.~Lundwall, W.~Pokapanich, H.~Bergersen, A.~Lindblad, T.~Rander, G.~\"Ohrwall,
  M.~Tchaplyguine, S.~Barth, U.~Hergenhahn, S.~Svensson, and O.~Bj\"orneholm.
\newblock Self-assembled heterogeneous argon/neon core-shell clusters studied
  by photoelectron spectroscopy.
\newblock {\em J. Chem. Phys.}, 126:214706, 2007.

\bibitem{Jahnke10}
T.~Jahnke, H.~Sann, T.~Havermeier, K.~Kreidi, C.~Stuck, M.~Meckel,
  M.~Sch{\"o}ffler, N.~Neumann, R.~Wallauer, S.~Voss, A.~Czasch, O.~Jagutzki,
  A.~Malakzadeh, F.~Afaneh, Th. Weber, H.~Schmidt-B{\"o}cking, and
  R.~D{\"o}rner.
\newblock {Ultrafast energy transfer between water molecules}.
\newblock {\em Nature Physics}, 6:139, 2010.

\bibitem{Forstel13}
M.~F{\"o}rstel, T.~Arion, and U.~Hergenhahn.
\newblock {Measuring the efficiency of interatomic Coulombic decay in Ne
  clusters}.
\newblock {\em J. Electron Spectrosc. Relat. Phenom.}, 191:16, 2013.

\bibitem{Mucke15}
M.~Mucke, T.~Arion, M.~F{\"o}rstel, T.~Lischke, and U.~Hergenhahn.
\newblock {Competition of inelastic electron scattering and Interatomic
  Coulombic Decay in Ne clusters}.
\newblock {\em J. Electron Spectrosc. Relat. Phenom.}, 200:232, 2015.

\bibitem{Fasshauer14_1}
E.~Fasshauer, M.~F\"orstel, S.~Pallmann, M.~Pernpointner, and U.~Hergenhahn.
\newblock Using icd for structure analysis of clusters: a case study on
  coexpanded ne-ar clusters.
\newblock {\em New J. Phys.}, 16:103026, 2014.

\bibitem{Zobeley98}
J.~Zobeley, L.~S. Cederbaum, and F.~Tarantelli.
\newblock Highly excited electronic states of molecular clusters and their
  decay.
\newblock {\em J. Chem. Phys.}, 108(23):9737, 1998.

\bibitem{Pernpointner06}
M.~Pernpointner, S.~Knecht, and L.~S. Cederbaum.
\newblock {Ionization spectra and electronic decay in small iodide clusters:
  Fully relativistic results}.
\newblock {\em J. Chem. Phys.}, 125:034309, 2006.

\bibitem{Mueller06}
I.~B. M{\"u}ller and L.~S. Cederbaum.
\newblock {Ionization and double ionization of small water clusters}.
\newblock {\em J. Chem. Phys.}, 125:204305, 2006.

\bibitem{Kryzhevoi11_1}
N.~V. Kryzhevoi and L.~S. Cederbaum.
\newblock {Using pH Value To Control Intermolecular Electronic Decay}.
\newblock {\em Angew. Chem. Int. Ed.}, 50:1306, 2011.

\bibitem{Ghosh13a}
A.~Ghosh, S.~Pal, and N.~Vaval.
\newblock {Study of interatomic Coulombic decay of Ne(H2O)n (n=1,3) clusters
  using equation-of-motion coupled-cluster method}.
\newblock {\em J. Chem. Phys.}, 139:064112, 2013.

\bibitem{Bande13}
A.~Bande.
\newblock Electron dynamics of interatomic coulombic decay in quantum dots
  induced by a laser field.
\newblock {\em J. Chem. Phys.}, 138:214104, 2013.

\bibitem{Harbach13}
P.~H.~P. Harbach, M.~Schneider, S.~Faraji, and A.~Dreuw.
\newblock Intermolecular coulombic decay in biology: the initial electron
  detachment from fadh- in dna photolyases.
\newblock {\em J. Phys. Chem. Lett.}, 4:943, 2013.

\bibitem{Alizadeh15}
E.~Alizadeh, T.~M. Orlando, and L.~Sanche.
\newblock {Biomolecular Damage Induced by Ionizing Radiation: The Direct and
  Indirect Effects of Low-Energy Electrons on DNA}.
\newblock {\em Annu. Rev. Phys. Chem.}, 66:379, 2015.

\bibitem{Gokhberg14}
K.~Gokhberg, P.~Koloren\v{c}, A.~I. Kuleff, and L.~S. Cederbaum.
\newblock {Site- and energy-selective slow-electron production through
  intermolecular Coulombic decay}.
\newblock {\em Nature}, 505:661, 2014.

\bibitem{Trinter14}
F.~Trinter, M.~S. Sch{\"o}ffler, H.~K. Kim, F.~P. Sturm, K.~Cole, N.~Neumann,
  A.~Vredenborg, J.~Williams, I.~Bocharova, R.~Guillemin, M.~Simon,
  A.~Belkacem, A.~L. Landers, Th. Weber, H.~Schmidt-B{\"o}cking, R.~D{\"o}rner,
  and Jahnke T.
\newblock {Resonant Auger decay driving intermolecular Coulombic decay in
  molecular dimers}.
\newblock {\em Nature}, 505:664, 2014.

\bibitem{Fasshauer13}
E.~Fasshauer, M.~Pernpointner, and K.~Gokhberg.
\newblock Interatomic decay of inner-valence ionized states in arxe clusters:
  Relativistic approach.
\newblock {\em J. Chem. Phys.}, 138:014305, 2013.

\bibitem{kryzhevoi2007}
N.~V. Kryzhevoi, V.~Averbukh, and L.~S. Cederbaum.
\newblock High activity of helium droplets following ionisation of systems
  inside those droplets.
\newblock {\em Phys. Rev. B}, 76:094513, 2007.

\bibitem{Fasshauer16_1}
E.~Fasshauer, M.~F\"orstel, M.~M\"ucke, M.~Pernpointner, and U.~Hergenhahn.
\newblock in preparation.

\bibitem{Hagena72}
O.~F. Hagena and W.~Obert.
\newblock Cluster formation in expanding supersonic jets: Effect of pressure,
  temperature, nozzle size, and test gas.
\newblock {\em The Journal of Chemical Physics}, 56(5):1793--1802, 1972.

\bibitem{Hagena81}
O.~F. Hagena.
\newblock Nucleation and growth of clusters in expanding nozzle flows.
\newblock {\em Surf. Sci.}, 106:101, 1981.

\bibitem{Hagena87}
O.~F. Hagena.
\newblock Condensation in free jets: Comparison of rare gases and metals.
\newblock {\em Z. Phys. D}, 4:291, 1987.

\bibitem{Benfield92}
R.~E. Benfield.
\newblock Mean coordination numbers and the non-metal-metal transition in
  clusters.
\newblock {\em J. Chem. Soc. Faraday Trans.}, 88:1107, 1992.

\bibitem{Hartke02}
B.~Hartke.
\newblock Structural transitions in clusters.
\newblock {\em Angew. Chem. Int. Ed.}, 41:1468, 2002.

\bibitem{Pahl08}
E.~Pahl, F.~Calvo, L.~Ko\v{c}i, and P.~Schwerdtfeger.
\newblock Accurate melting temperatures for neon and argon from ab initio monte
  carlo simulations.
\newblock {\em Angew. Chem. Int. Ed.}, 47:8207, 2008.

\bibitem{Wentzel27}
G.~Wentzel.
\newblock {\"U}ber strahlungslose quantenspr{\"u}nge.
\newblock {\em Z. Physik}, 43:524, 1927.

\bibitem{Feshbach58}
H.~Feshbach.
\newblock Unified theory of nuclear reactions.
\newblock {\em Ann. Phys.}, 5:357, 1958.

\bibitem{Feshbach62}
H.~Feshbach.
\newblock A unified theory of nuclear reactions. ii.
\newblock {\em Ann. Phys.}, 19:287, 1962.

\bibitem{Fano61}
U.~Fano.
\newblock Effects of configuration interaction on intensities and phase shifts.
\newblock {\em Phys. Rev.}, 124(6):1866--1878, Dec 1961.

\bibitem{Averbukh05}
V.~Averbukh and L.~S. Cederbaum.
\newblock Ab initio calculation of interatomic decay rates by a combination of
  the fano ansatz, green's-function methods, and the stieltjes imaging
  technique.
\newblock {\em J. Chem. Phys.}, 123:204107, 2005.

\bibitem{Fasshauer15_1}
E.~Fasshauer, P.~Koloren\ifmmode~\check{c}\else \v{c}\fi{}, and
  M.~Pernpointner.
\newblock Relativistic decay widths of autoionization processes: The
  relativistic fanoadc-stieltjes method.
\newblock {\em J. Chem. Phys.}, 142:144106, 2015.

\bibitem{Bondi64}
A.~Bondi.
\newblock van der waals volumes and radii.
\newblock {\em J. Phys. Chem.}, 68:441, 1964.

\bibitem{HARDRoC}
{HARDRoC}, Hunting Asymptotic Relativistic Decay Rates of Clusters (2013),
  written by E.~Fasshauer (see
  http://www.pci.uni-heidelberg.de/tc/usr/elke/hardroc/html/main.html).

\bibitem{Fasshauer_thesis}
E.~Fasshauer.
\newblock {\em Investigation of Relativistic Effects in Electronic Decay
  Processes in Small and Large Noble Gas Clusters by Ab Initio and New
  Simulation Approaches}.
\newblock PhD thesis, University of Heidelberg, 2014.

\bibitem{Scheit06}
S.~Scheit, V.~Averbukh, H.-D. Meyer, J.~Zobeley, and L.~S. Cederbaum.
\newblock {Interatomic Coulombic decay in a heteroatomic rare gas cluster}.
\newblock {\em J. Chem. Phys.}, 124:154305, 2006.

\bibitem{OKeeffe14}
P.~O'Keeffe, A.~Ciavardini, E.~Ripani, P.~Bolognesi, M.~Coreno, L.~Avaldi,
  M.~Devetta, M.~Di~Fraia, C.~Callegari, K.~C. Prince, and R.~Richter.
\newblock {Experimental investigation of the interatomic Coulombic decay in
  NeAr dimers}.
\newblock {\em Phys. Rev. A}, 90:042508, 2014.

\bibitem{Schnorr13}
K.~Schnorr, A.~Senftleben, M.~Kurka, A.~Rudenko, L.~Foucar, G.~Schmid,
  A.~Broska, T.~Pfeifer, K.~Meyer, D.~Anielski, R.~Boll, D.~Rolles,
  M.~K{\"u}bel, M.~F. Kling, Y.~H. Jiang, S.~Mondal, T.~Tachibana, K.~Ueda,
  T.~Marchenko, M.~Simon, G.~Brenner, R.~Treusch, S.~Scheit, V.~Averbukh,
  J.~Ullrich, C.~D. Schr{\"o}ter, and R.~Moshammer.
\newblock {Time-Resolved Measurement of Interatomic Coulombic Decay in Ne$_2$}.
\newblock {\em Phys. Rev. Lett.}, 111:093402, 2013.

\bibitem{Schnorr15}
K.~Schnorr, A.~Senftleben, G.~Schmid, S.~Augustin, M.~Kurka, A.~Rudenko,
  L.~Foucar, A.~Broska, K.~Meyer, D.~Anielski, D.~Anielski, R.~Boll, D.~Rolles,
  M.~K{\"u}bel, M.~F. Kling, Y.~H. Jiang, S.~Mondal, T.~Tachibana, K.~Ueda,
  T.~Marchenko, M.~Simon, G.~Brenner, R.~Treusch, S.~Scheit, V.~Averbukh,
  J.~Ullrich, T.~Pfeifer, C.~D. Schr{\"o}ter, and R.~Moshammer.
\newblock {Time-resolved study of ICD in Ne dimers using FEL radiation}.
\newblock {\em J. Electron Spectrosc. Relat. Phenom.}, 204:245, 2015.

\bibitem{Barth06_2}
S.~Barth, S.~Marburger, O.~Kugeler, V.~Ulrich, S.~Joshi, A.~M. Bradshaw, and
  U.~Hergenhahn.
\newblock {The efficiency of Interatomic Coulombic Decay in Ne clusters}.
\newblock {\em Chem. Phys.}, 329:246, 2006.

\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2016-03-17 revised/abstract.tex
format of the paper - prepare submission

--- 2016-01-10 abstract.tex
@@
 non-nearest neighbours is highlighted. In the neon clusters, the lifetime of the
-bulk atoms is found to be in excellent agreement with experiment, while the
+bulk atoms is found to be in excellent agreement with experiment
+(\emph{Phys. Rev. Lett.}, \textbf{93}, 173401 (2004).), while the
 lifetimes of the surface atoms differ significantly. Hence, the experimental

### 2016-03-17 revised/computational.tex
format of the paper - prepare submission

--- 2016-01-10 computational.tex
@@
 shells. These are based on the van der Waals radii for neon
-$r_{Ne}=\unit[1.54]{\AA}$
-and argon $r_{Ar}=\unit[1.88]{\AA}$ \cite{Bondi64}.
+$r_{Ne}=$ \unit[1.54]{\AA}
+and argon $r_{Ar}=$ \unit[1.88]{\AA} \cite{Bondi64}.
 In case of the NeAr clusters two of those
@@
 
-The calculations to obtain the ICD electron spectra of those cluster
+The calculations to obtain the ICD electron spectra of all cluster
 structures were performed with
-the program HARDRoC \cite{HARDRoC} using experimental ionization energies shown
+the program HARDRoC \cite{HARDRoC} based on the decomposition of the cluster into
+pairs. Every pair with the same distance is treated equally. This includes the
+assumption that every neon atom is ionized with the same probability.
+\cite{Fasshauer14_1,Fasshauer_thesis}
+It uses experimental ionization energies shown
 in Table \ref{table:exp_input} and curves fitted to the decay width of the

### 2016-03-17 revised/summary.tex
format of the paper - prepare submission

--- 2015-12-07 summary.tex
@@
 We have discussed two of the three aspects one needs to take into account
-to simulate the ICD spectrum of rare gas clusters in detail. Due to the nature
+to simulate the ICD spectrum of rare gas clusters properly. Due to the nature
 of clusters, a neon atom ionized in the inner-valence will have several decay
-partners at different distances. The larger the interatomic distance the higher
+partners at different distances. The larger the interatomic distance is the higher
 is the kinetic energy of the ICD electrons which will yield a multitude of
@@
 This leads to a different number of peaks in the spectra which might help to
-differentiate between clusters of icosahedral and cuboctahedral cluster structure.
+distinguish between clusters of icosahedral and cuboctahedral cluster structure.
 
@@
 with experiment, the lifetimes of the surface atoms differ significantly.
-Assuming the experimentally determined lifetime to be correct, this deviation
+This deviation
 might be caused by different static cluster structures than taken into account
